---
title: "RDBES Catch and Effort Overview"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output: html_document

# output: 
#   prettydoc::html_pretty:
#     theme: tactile
#     highlight: vignette
#     toc: yes
#     toc_depth: 3 
#     fig_height: 7
#     fig_width: 10
#     #css: styles.css
    
params:
  set_subtitle: "Title"
  region: NA
  year: NA
  logo_path: NA
  data_dir: NA
  
---

---
subtitle: `r paste(params$region, params$year, sep = ", ")`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo=FALSE}
  htmltools::img(src = knitr::image_uri(params$logo_path), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
```

```{r loadPackages, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD PACKAGES AND DEFINE EVAL_PARAMETERS IF NEEDED

# library(tidyverse)
# library(car)
# library(ggrepel)
# library(knitr)
# library(kableExtra)
# library(data.table)
# library(magrittr)
# library(plotly)
# library(leaflet)

 ## establish conditions  - can use it if for example some chunks should be run only for selected Regions, e.g. only Bal
 eval_region <- params$region=='Baltic' # when added to the chunk header, the chunk will be run only for Baltic report

```


```{r GlobalSettings, echo=FALSE}
# DEFINE GLOBAL PARAMETERS/FUNCTIONS FOR DISPLAYING TABLES/PLOTS/MAPS/...

```

```{r loadPrepareData, echo=FALSE}
# LOAD AND PREPARE DATA

```

```{r fleetRegisterData, echo=FALSE}
# LOAD AND PREPARE FLEET REGISTER DATA

```


**Disclaimer**
put some text here

# Introduction
put some text here

## Reading the graphs
### Barplots
put some text here

### Maps
put some text here

# Overall fleet evolution (All RCGs){.tabset}

## Number of vessels
**Table 1.**put some text here
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

```

## Power
**Table 2.** put some text here
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

```

## Gross tonnage
**Table 3.** put some text here
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

```

## {-}

# Landings (CL)

## Overall landings{.tabset}

### Landings by species
### Landings by species and country
### {-}

### Landings by catch_group
### Landings by catch_group

### Landings by fleet

### Landings by area

### Landings by metier

### Landings by harbour

### Landings abroad

### Spatial distribution of landings


## Small pelagics landings

### Landings by country, small pelagics

### Landings by species, small pelagics

### Landings by fleet, small pelagics

### Landings by area, small pelagics

### Landings by metier, small pelagics

### Landings by harbour, small pelagics

### Landings abroad, small pelagics

### Spatial distribution of landings, small pelagics


## Demersal landings (without flatfish)

### Landings by country, demersal (without flatfish)

### Landings by species, demersal (without flatfish)

### Landings by fleet, demersal (without flatfish)

### Landings by area, demersal (without flatfish)

### Landings by metier, demersal (without flatfish)

### Landings by harbour, demersal (without flatfish)

### Landings abroad, demersal (without flatfish)

### Spatial distribution of landings, demersal (without flatfish)


## Flatfish landings

### Landings by country, flatfish

### Landings by species, flatfish

### Landings by fleet, flatfish

### Landings by area, flatfish

### Landings by metier, flatfish

### Landings by harbour, flatfish

### Landings abroad, flatfish

### Spatial distribution of landings, flatfish


# Effort (CE)

## Effort by country

## Effort by fleet

## Effort by area{.tabset}
### Below 10 meters
### 10 meteres and above
### {-}

## Effort by metier {.tabset}
### Below 10 meters
### 10 meteres and above
### {-}

## Effort by harbour {.tabset}
### Below 10 meters
### 10 meteres and above
### {-}

## Spatal distribution on effort {.tabset}
### Below 10 meters
### 10 meteres and above
### {-}

## Appendix A. Dates of data extraction
## Appendix B. Catch groups
## Appendix C. Mean Landings per stock, put years here
## Appendix D. Summary information of the landings abroad (ton), by country and area
## Appendix E. Glossary for the country codes

