---
author: "ISSG Metier Overviews"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    smoothScrollSpeed: "fast"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile,
  encoding = encoding, 
  output_file = file.path(dirname(inputFile), "BALT_2023.html"))}) # <--- Change region here; Change year here (2021;2022;2023)
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = NA, fig.dim = c(14, 10))
options(scipen=999)
knitr::opts_knit$set(root.dir = "C:/Users/dema008/Desktop/Mariana/ISSG Metier and transversable variables/Data") # <----- add working directory
```

```{r}
library(tidyverse, quietly=TRUE, warn.conflicts=FALSE)
library(knitr)
library(ggplot2)
library(cowplot)
library(pander)
library(ggpubr)
library(kableExtra)
library(sf)
library(rnaturalearth)
library(RColorBrewer)
library(data.table)
```

```{r}
# Set RCG region - NSEA, NAtl, BALT
rr <- "BALT" # <---------- and here 
year <- 2023 # <---------- change year here

if(rr %in% "NSEA"){
  title <- paste("North Sea and Eastern Arctic -", year)
}else if(rr %in% "NAtl"){
  title <- paste("North Atlantic -", year)
}else{
  title <- paste("Baltic -", year)
}

```

---
title: "`r title`"
---


```{r}
# Reference lists 
## Scientific name 
urls <- "https://raw.githubusercontent.com/ices-eg/RCGs/master/Metiers/Scripts/ICESVocabSpecies/ICESVocabAphiaIDScienName_2023.csv"
ScienName <- read.csv(urls, header = TRUE)


### Remove deprecated and invalid records 
ScienName <- filter(ScienName, !Deprecated %in% c("", "True", "2020-09-16")) %>%
  select(Code, Description) %>%
  mutate(Code = as.numeric(Code))
## Area - region (normal path gives back xml version)
url <- "https://raw.githubusercontent.com/ices-eg/RCGs/master/Metiers/Reference_lists/AreaRegionLookup.csv"
Area <- read.csv(url, header = TRUE)
### Fix the extra space in rcg region code
Area <- mutate(Area, Code = ifelse(Code %in% "NSEA                                    " , "NSEA",
                             ifelse(Code %in% "NAtl                                      ", "NAtl", Code))) %>%
  select(AreaCode, Code)

### Shapefiles 
### Need to source it from online - Can't open it
# rect <- read_sf("https://raw.githubusercontent.com/ices-eg/RCGs/Metiers/Scripts/RectangleShapefiles/StatRec_map_Areas_Full_20170124.shp")

#rect <- read_sf("C:/Users/molla004/OneDrive - Wageningen University & #Research/Git/hub/RCGs/Metiers/Scripts/RectangleShapefiles/StatRec_map_Areas_Full_20170124.shp")

rect <- read_sf("./StatRec_map_Areas_Full_20170124.shp")
world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)
```

```{r}
# Read data 

CL<-fread("./CommercialLanding.csv", quote = "")  
CE<-fread("./CommercialEffort.csv", quote="")

# Filter year (2021, 2022, 2023)
CL <- subset(CL, CLyear == "2023") # <---------- change year here
CE <- subset(CE, CEyear == "2023") # <---------- change year here

```

```{r}
# Select only area 27 
CL <- filter(CL, substr(CLarea, 1, 2) %in% "27")
CE <- filter(CE, substr(CEarea, 1, 2) %in% "27")

# Assign regions (and split? Need to do this at the end of processing then)
CL <- left_join(CL, Area, by = c("CLarea" = "AreaCode"))
#table(CL$Code, useNA = "always") # 6 NAs from area 27 (IE, GB) - exclude for now, check!!!  
                                  # 5 NAS 2021; 1 NA 2022; 13 NAS 2023
CL <- filter(CL, !is.na(Code))

CE <- left_join(CE, Area, by = c("CEarea" = "AreaCode"))
#table(CE$Code, useNA = "always") # No NA's
```

```{r}
# Merge for scientific name 
CL <- left_join(CL, ScienName, by = c("CLspeciesCode" = "Code"))
```


```{r}
# Process

## Year string 
CL$CLyear <- as.character(CL$CLyear)
CE$CEyear <- as.character(CE$CEyear)

## Month factors 
CL$CLmonth <- factor(CL$CLmonth, levels = as.character(c(1:12)))
CE$CEmonth <- factor(CE$CEmonth, levels = as.character(c(1:12)))

## Quarter factors 
CL$CLquarter <- factor(CL$CLquarter, levels = as.character(c(1:4)))
CE$CEquarter <- factor(CE$CEquarter, levels = as.character(c(1:4)))

## Vessel length factors 
CL$CLvesLenCat <- factor(CL$CLvesselLengthCategory, levels = c("VL0006","VL0608", "VL0810", "VL1012", "VL1215", "VL1518", "VL1824", "VL2440", "VL40XX", "NK"))
CE$CEvesLenCat <- factor(CE$CEvesselLengthCategory, levels = c("VL0006","VL0608", "VL0810", "VL1012", "VL1215", "VL1518", "VL1824", "VL2440", "VL40XX", "NK"))

## Country factors 
CL$CLvesselFlagCountry <- factor(CL$CLvesselFlagCountry, levels = sort(unique(CL$CLvesselFlagCountry)))
CE$CEvesselFlagCountry <- factor(CE$CEvesselFlagCountry, levels = sort(unique(CE$CEvesselFlagCountry)))


## Get metier lvl 4 
CL <- mutate(CL, CLmetier4 = str_extract(CLmetier6, "[^_]+"))
CE <- mutate(CE, CEmetier4 = str_extract(CEmetier6, "[^_]+"))

## Get metier lvl 5 
CL <- mutate(CL, CLmetier5 = str_extract(CLmetier6,  "[^_]*_[^_]*"))
CE <- mutate(CE, CEmetier5 = str_extract(CEmetier6,  "[^_]*_[^_]*"))


# Weight kg to t 
CL <- mutate(CL, CLscientificWeight = round(CLscientificWeight/1000, digits = 2))

# Filter CatchCategory == Landings
CL <- filter(CL, CLcatchCategory %in% "Lan")

```


```{r}
# Filter by area 
CLAREA <- filter(CL, Code %in% rr)

CEAREA <- filter(CE, Code %in% rr)

```


```{r}
# Set country colors
ct.cols <- 14 
myColors <- colorRampPalette(brewer.pal(8, "Set2"))(ct.cols)
names(myColors) <- levels(CL$CLvesselFlagCountry)
colScale <- scale_fill_manual(name = "CLvesselFlagCountry",values = myColors)

```


```{r}
# Top 10 metiers by region based on FISHING DAYS 
# Select top 10 lvl 4 
# Select top 10 metier lvl 5 from the top 10 metier lvl 4
# Select top 5 metier lvl 6 from the top 10 metier lvl 5 
#--- Keep all metier lvl 5 and metier lvl 6 for the respective summary plots  

# TODO - more than 5% of total fishing days and less than 10/5

# Lvl 4 
CEtop4 <- CEAREA %>%
  group_by(CEmetier4) %>%
  summarise(Fd = sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
  mutate(ToTfd = sum(Fd),
         Perc = (Fd/ToTfd)*100)%>%
  top_n(10, Perc)

CEAREA4 <- filter(CEAREA, CEmetier4 %in% unique(CEtop4$CEmetier4))

# Lvl 5 
CEtop5 <- CEAREA4 %>%
  group_by(CEmetier4, CEmetier5) %>%
  summarise(Fd = sum(CEscientificDaysAtSea, na.rm = TRUE))  %>%
  mutate(ToTfd = sum(Fd),
         Perc = (Fd/ToTfd)*100) %>%
  filter(Perc > 5)

CEAREA5 <- filter(CEAREA4, CEmetier5 %in% unique(CEtop5$CEmetier5))


# Lvl 6 - top 5
CEtop6 <- CEAREA5 %>%
  group_by(CEmetier4, CEmetier5, CEmetier6) %>%
  summarise(Fd = sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
  mutate(ToTfd = sum(Fd),
         Perc = (Fd/ToTfd)*100) %>%
  filter(Perc > 5)

# Arrange based on index mesh size
CEtop6$mesh1 <- sapply(str_split(CEtop6$CEmetier6, fixed("_")), "[", 3)
CEtop6$mesha <- as.numeric(sapply(str_extract_all(CEtop6$mesh1, "\\d+"), "[", 1))
CEtop6 <- mutate(CEtop6, mesha = as.numeric(mesha))
CEtop6 <- CEtop6 %>%
  arrange(CEmetier4, CEmetier5, mesha)


# Lvl 6 
CEAREA6 <- filter(CEAREA5, CEmetier6 %in% unique(CEtop6$CEmetier6))
CLAREA4 <- filter(CLAREA, CLmetier4 %in% unique(CEtop4$CEmetier4))
CLAREA5 <- filter(CLAREA4, CLmetier5 %in% unique(CEtop5$CEmetier5))
CLAREA6 <- filter(CLAREA5, CLmetier6 %in% unique(CEtop6$CEmetier6))
```


# Summary 

This report presents the description of the main metiers in the `r title`. The data used to produce the report is from the ‘Commercial Landings’ (CL) and ‘Commercial Effort’ (CE) tables submitted to the RDBES in 2024. The description of the metiers includes information on scientific landings (weight and value) and scientific effort (number of fishing days and number of trips), by country, metier and vessel size range. The CL information presented in this report refers only to the catch category for the landings (‘Lan’), ignoring the other possible options (e.g. ‘BMS’ and ‘RegDis’). The information is displayed in an hierarchical mode, from the lowest (level 4) to the highest (level 6) metier. The top 10 metiers at level 4 are selected according to the scientific effort in number of fishing days. The metiers at levels 5 and 6 presented in this report are the ones that have more than 5% of the total fishing days within the previous metier level. It is important to note that if scientific landing weight was considered for selecting the main metiers (instead of the effort), probably other important metiers might also be included in these descriptions.


# All metier level 4 

The landings and effort overview of all metiers at level 4 present in the North Atlantic are displayed in the set of figures below.



```{r}
  
  #have an error here since the current CLAREA/CL datasets don't have a column called "CLtotalOfficialLandingsValue". The only column I     found is "CLlandingsValue" so I am updating the following code:
  ## Table totals by country 
    tab1 <- CLAREA %>% 
    group_by(CLmetier4) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE), 
              CLlandingsValue = sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    rename(Metier4 = CLmetier4)

  
    #CEnumberOfFractionTrips is now called CEnumberOfFractionalTrips,so I am going to update the following code:
    tab2 <-CEAREA %>%
    group_by(CEmetier4) %>%
    summarise(CEscientificDaysAtSea= sum(CEscientificDaysAtSea, na.rm = TRUE),
              CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    rename(Metier4 = CEmetier4)
  
  left_join(tab1, tab2) %>%
          rename(ScientificWeight = CLscientificWeight,
                 Value = CLlandingsValue,
                 ScientificFishingDays = CEscientificDaysAtSea,
                 NumberOfTrips = CEnumberOfFractionalTrips) %>%
    kbl(caption = "Total values by metier level 4") %>%
      kable_styling()
```


```{r}



  p1 <- CLAREA %>%
    group_by(CLmetier4, CLvesselFlagCountry) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE)) %>%
    group_by(CLmetier4) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot( aes(reorder(CLmetier4, -TotW), CLscientificWeight, fill = CLvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    colScale +
    xlab("Metier lvl 4") +
    ylab("Weight (t)") +    
    ggtitle("Landed weight (t) by country and metier level 4") 
  
  p2 <- CLAREA %>%
    group_by(CLmetier4, CLvesselFlagCountry) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    group_by(CLmetier4) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot( aes(x= reorder(CLmetier4, -TotL), y=CLlandingsValue, fill =  CLvesselFlagCountry)) +     
    geom_bar(stat = "identity") +
    xlab("Metier lvl 4") +
    ylab("Value in €") +
    ggtitle("Landed value (€) by country and metier level 4") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    colScale 
  
  # CE 
  
  k1 <- CEAREA %>%
    group_by(CEmetier4, CEvesselFlagCountry) %>%
    summarise(CEscientificDaysAtSea= sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
    group_by(CEmetier4) %>%
    mutate(TotD = sum(CEscientificDaysAtSea)) %>%
    ggplot( aes(reorder(CEmetier4, -TotD),CEscientificDaysAtSea, fill = CEvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 4") +
    ylab("Scientific fishing days") +
    ggtitle("Fishing days by country and metier level 4")  +
    colScale
  
  k2 <- CEAREA %>%
    group_by(CEmetier4, CEvesselFlagCountry) %>%
    summarise(CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    group_by(CEmetier4) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>% 
    ggplot( aes(reorder(CEmetier4, -TotD),CEnumberOfFractionalTrips, fill = CEvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    xlab("Metier lvl 4") +
    ylab("Number of trips") +
    ggtitle("Number of trips by country and metier level 4")  +
    colScale
  
  l <- ggarrange(p1, p2, k1, k2, ncol = 2, nrow = 2)
  print(l)
  
  # Vessel length category 
  
  vl1 <- CLAREA %>%
    group_by(CLmetier4, CLvesLenCat) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE)) %>%
    group_by(CLmetier4) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot( aes(reorder(CLmetier4, -TotW), CLscientificWeight, fill = CLvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 4") +
    ylab("Weight (t)") +
    ggtitle("Landed weight (t) by vessel length category and metier level 4") 
  
  vl2 <- CLAREA %>%
    group_by(CLmetier4, CLvesLenCat) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    group_by(CLmetier4) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot( aes(x= reorder(CLmetier4, -TotL), y=CLlandingsValue, fill =  CLvesLenCat)) +     
    geom_bar(stat = "identity") +
    xlab("Metier lvl 4") +
    ylab("Value in €") +
    ggtitle("Landed value (€) by vessel length category and metier level 4") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
  
  # CE 
  
  vl3 <- CEAREA %>%
    group_by(CEmetier4, CEvesLenCat) %>%
    summarise(CEscientificDaysAtSea= sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
    group_by(CEmetier4) %>%
    mutate(TotD = sum(CEscientificDaysAtSea)) %>%
    ggplot( aes(reorder(CEmetier4, -TotD),CEscientificDaysAtSea, fill = CEvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 4") +
    ggtitle("Fishing days by vessel length category and metier level 4")  
  
  vl4 <- CEAREA %>%
    group_by(CEmetier4, CEvesLenCat) %>%
    summarise(CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    group_by(CEmetier4) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>% 
    ggplot( aes(reorder(CEmetier4, -TotD),CEnumberOfFractionalTrips, fill = CEvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    xlab("Metier lvl 4") +
    ggtitle("Number of trips by vessel length category and metier level 4")  
  
  vlf <- ggarrange(vl1, vl2, vl3, vl4, ncol = 2, nrow = 2)
  print(vlf)
  

```


# Top 10 metier level 4 


```{r}

# Metier lvl 4 section 
create_section4 <- function(met4, CEAREA, CLAREA) {

  # Header
  pander::pandoc.header(met4, level = 2)
  

  ### HOW TO ADD TEXT IN SUBSECTION 
   # pandoc.p("You can add text like this")
   # 
   # ## if you want to make it specific 
   # if(met4 %in% "FPN"){
   #     pandoc.p("Adds text only under the FPN section")
   # }
   # 
  
  # Section contents
  # Flag country 
  # CL 
  
  p1 <- CLAREA %>%
    filter(CLmetier4 %in% met4) %>%
    group_by(CLmetier5, CLvesselFlagCountry) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE)) %>%
    group_by(CLmetier5) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot( aes(reorder(CLmetier5, -TotW), CLscientificWeight, fill = CLvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 5") +
    ylab("Weight (t)") +
    ggtitle(paste0("Landed weight (t) by country (",met4, ")" )) +
    colScale 
  
  p2 <- CLAREA %>%
    filter(CLmetier4 %in% met4) %>%
    group_by(CLmetier5, CLvesselFlagCountry) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    group_by(CLmetier5) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot( aes(x= reorder(CLmetier5, -TotL), y=CLlandingsValue, fill =  CLvesselFlagCountry)) +     
    geom_bar(stat = "identity") +
    xlab("Metier lvl 5") +
    ylab("Value in €") +
    ggtitle(paste0("Landed value (€) by country (",met4, ")")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    colScale 
  
  # CE 
  
  k1 <- CEAREA %>%
    filter(CEmetier4 %in% met4) %>%
    group_by(CEmetier5, CEvesselFlagCountry) %>%
    summarise(CEscientificDaysAtSea= sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
    group_by(CEmetier5) %>%
    mutate(TotD = sum(CEscientificDaysAtSea)) %>%
    ggplot( aes(reorder(CEmetier5, -TotD),CEscientificDaysAtSea, fill = CEvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 5") +
    ggtitle(paste0("Fishing days by country (", met4,")")) +
    colScale 
  
  k2 <- CEAREA %>%
    filter(CEmetier4 %in% met4) %>%
    group_by(CEmetier5, CEvesselFlagCountry) %>%
    summarise(CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    group_by(CEmetier5) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>% 
    ggplot( aes(reorder(CEmetier5, -TotD),CEnumberOfFractionalTrips, fill = CEvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    xlab("Metier lvl 5") +
    ggtitle(paste0("Number of trips by country (", met4, ")")) +
    colScale 
  
  l <- ggarrange(p1, p2, k1, k2, ncol = 2, nrow = 2)
  print(l)
  
  cat("\n")
  cat("\n")
  
  # Vessel length category 
  
  vl1 <- CLAREA %>%
    filter(CLmetier4 %in% met4) %>%
    group_by(CLmetier5, CLvesLenCat) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE)) %>%
    group_by(CLmetier5) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot( aes(reorder(CLmetier5, -TotW), CLscientificWeight, fill = CLvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 5") +
    ylab("Weight (t)") +
    ggtitle(paste0("Landed weight (t) by vessel length category (", met4,")")) 
  
  vl2 <- CLAREA %>%
    filter(CLmetier4 %in% met4) %>%
    group_by(CLmetier5, CLvesLenCat) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    group_by(CLmetier5) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot( aes(x= reorder(CLmetier5, -TotL), y=CLlandingsValue, fill =  CLvesLenCat)) +     
    geom_bar(stat = "identity") +
    xlab("Metier lvl 5") +
    ylab("Value in €") +
    ggtitle(paste0("Landed value (€) by vessel length category (", met4, ")")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
  
  # CE 
  
  vl3 <- CEAREA %>%
    filter(CEmetier4 %in% met4) %>%
    group_by(CEmetier5, CEvesLenCat) %>%
    summarise(CEscientificDaysAtSea= sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
    group_by(CEmetier5) %>%
    mutate(TotD = sum(CEscientificDaysAtSea)) %>%
    ggplot( aes(reorder(CEmetier5, -TotD),CEscientificDaysAtSea, fill = CEvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 5") +
    ggtitle(paste0("Fishing days by vessel length category (", met4, ")")) 
  
  vl4 <- CEAREA %>%
    filter(CEmetier4 %in% met4) %>%
    group_by(CEmetier5, CEvesLenCat) %>%
    summarise(CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    group_by(CEmetier5) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>% 
    ggplot( aes(reorder(CEmetier5, -TotD),CEnumberOfFractionalTrips, fill = CEvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    xlab("Metier lvl 5") +
    ggtitle(paste0("Number of trips by vessel length category (", met4,")")) 
  
  vlf <- ggarrange(vl1, vl2, vl3, vl4, ncol = 2, nrow = 2)
  print(vlf)
  
  # empty lines to be sure that this is valid Markdown
  pander::pandoc.p('')
  
}

```

```{r}

# Metier lvl 5 section 
create_section5 <- function(met5, CEAREA4, CLAREA4) {

   # Header
   pander::pandoc.header(met5, level = 3)
  
    pandoc.p(" Summary table with information on the Scientific landings and fishing effort of all the metiers at level 5, by flag country.")

  
  CLAREA4 <- filter(CLAREA4, CLmetier5 %in% met5)
  CEAREA4 <- filter(CEAREA4, CEmetier5 %in% met5)

  

  # Section contents
  
  ## Table totals by country 
    tab1 <- CLAREA4 %>% 
    group_by(CLmetier5, CLvesselFlagCountry) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight), 
              CLlandingsValue = sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    rename(Metier5 = CLmetier5, 
           VesselFlagCountry = CLvesselFlagCountry)
  
  tab2 <-CEAREA4 %>%
    group_by(CEmetier5, CEvesselFlagCountry) %>%
    summarise(CEscientificDaysAtSea= sum(CEscientificDaysAtSea, na.rm = TRUE),
              CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips)) %>%
    rename(Metier5 = CEmetier5, 
           VesselFlagCountry = CEvesselFlagCountry)
  
  print(fintab <- left_join(tab1, tab2) %>%
          rename(ScientificWeight = CLscientificWeight,
                 Value = CLlandingsValue,
                 ScientificFishingDays = CEscientificDaysAtSea,
                 NumberOfTrips = CEnumberOfFractionalTrips) %>%
    filter(Metier5 %in% met5) %>%
    kbl(caption = "Total values by country and metier level 5") %>%
      kable_styling())
  
  
   ## CL 
  
    CLtop10 <- CLAREA4 %>%
    group_by(Description) %>%
    summarise(ToTw = sum(CLscientificWeight,na.rm = TRUE)) %>%
    top_n(10, ToTw ) %>%
    mutate(x = "x")
  
  CLtopSp <- left_join(CLAREA4, CLtop10, by = "Description") %>%
    mutate(Description = ifelse(is.na(x), "Others", Description))
  
  
  p1 <- CLAREA4 %>%
    group_by(CLmetier6, CLvesselFlagCountry) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight,na.rm = TRUE)) %>%
    group_by(CLmetier6) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot( aes(reorder(CLmetier6, -TotW), CLscientificWeight, fill = CLvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 6") +
    ylab("Weight (t)") +
    ggtitle(paste0("Landed weight (t) by country (", met5,")"))  +
    colScale
  
  p2 <- CLAREA4 %>%
    group_by(CLmetier6, CLvesselFlagCountry) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
      group_by(CLmetier6) %>%
    mutate(TotL = sum(as.numeric(CLlandingsValue))) %>%
    ggplot( aes(x= reorder(CLmetier6, -TotL), y=CLlandingsValue, fill =  CLvesselFlagCountry)) +     
    geom_bar(stat = "identity") +
    xlab("Metier lvl 6") +
    ylab("Value in €") +
    ggtitle(paste0("Landed value (€) by country (", met5,")")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    colScale
  
  # CE 
  
  k1 <- CEAREA4 %>%
    group_by(CEmetier6, CEvesselFlagCountry) %>%
    summarise(CEscientificDaysAtSea= sum(CEscientificDaysAtSea,na.rm = TRUE)) %>%
    group_by(CEmetier6) %>%
    mutate(TotD = sum(CEscientificDaysAtSea)) %>%
    ggplot( aes(reorder(CEmetier6, -TotD),CEscientificDaysAtSea, fill = CEvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 6") +
    ggtitle(paste0("Fishing days by country (", met5, ")"))  +
    colScale
  
  k2 <- CEAREA4 %>%
    group_by(CEmetier6, CEvesselFlagCountry) %>%
    summarise(CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips,na.rm = TRUE)) %>%
    group_by(CEmetier6) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>% 
    ggplot( aes(reorder(CEmetier6, -TotD),CEnumberOfFractionalTrips, fill = CEvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    xlab("Metier lvl 6") +
    ggtitle(paste0("Number of trips by country (", met5, ")"))  +
    colScale
  
  l <- ggarrange(p1, p2, k1, k2, ncol = 2, nrow = 2)
  print(l)
  
   # Vessel length category 
  
  vl1 <- CLAREA4 %>%
    group_by(CLmetier6, CLvesLenCat) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight,na.rm = TRUE)) %>%
    group_by(CLmetier6) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot( aes(reorder(CLmetier6, -TotW), CLscientificWeight, fill = CLvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 6") +
    ylab("Weight (t)") +
    ggtitle(paste0("Landed weight (t) by vessel length category (", met5,")"))  
  
  vl2 <- CLAREA4 %>%
    group_by(CLmetier6, CLvesLenCat) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    group_by(CLmetier6) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot( aes(x= reorder(CLmetier6, -TotL), y=CLlandingsValue, fill =  CLvesLenCat)) +     
    geom_bar(stat = "identity") +
    xlab("Metier lvl 6") +
    ylab("Value in €") +
    ggtitle(paste0("Landed value (€) by vessel length category (", met5,")")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
  
  # CE 
  
  vl3 <- CEAREA4 %>%
    group_by(CEmetier6, CEvesLenCat) %>%
    summarise(CEscientificDaysAtSea= sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
    group_by(CEmetier6) %>%
    mutate(TotD = sum(CEscientificDaysAtSea)) %>%
    ggplot( aes(reorder(CEmetier6, -TotD),CEscientificDaysAtSea, fill = CEvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 6") +
    ggtitle(paste0("Fishing days by vessel length category (", met5,")")) 
  
  vl4 <- CEAREA4 %>%
    group_by(CEmetier6, CEvesLenCat) %>%
    summarise(CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    group_by(CEmetier6) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>% 
    ggplot( aes(reorder(CEmetier6, -TotD),CEnumberOfFractionalTrips, fill = CEvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    xlab("Metier lvl 6") +
    ggtitle(paste0("Number of trips by vessel length category (", met5,")")) 
  
  vlf <- ggarrange(vl1, vl2, vl3, vl4, ncol = 2, nrow = 2)
  print(vlf)

 ### Weight
  w <- CLtopSp %>%
    group_by(CLmetier6, Description) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE)) %>%
    group_by(CLmetier6) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot(aes(reorder(CLmetier6, -TotW ), CLscientificWeight, fill = Description)) +
    geom_bar(stat = "identity")    +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(text = element_text(size = 15)) +
    xlab("Metier level 6") +
    ylab("Weight (t)") +
    ggtitle(paste0("Landed weight (t) top 10 species (", met5,")"))

  
  ### Value 
  l <- CLtopSp %>%
    group_by(CLmetier6,Description) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    group_by(CLmetier6) %>%
    mutate(TotL = sum(as.numeric(CLlandingsValue), na.rm =TRUE)) %>%
    ggplot(aes(reorder(CLmetier6, -TotL), CLlandingsValue, fill = Description)) +
    geom_bar(stat = "identity")    +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(text = element_text(size = 15)) +
    xlab("Metier level 6")+
    ylab("Value in €") +
    ggtitle(paste0("Landed value (€) top 10 species (", met5,")"))

  
  lw <- ggarrange(w, l, ncol = 2, nrow = 1)
  print(lw)
  
  
  # empty lines to be sure that this is valid Markdown
   pander::pandoc.p('')

}

```

```{r}
# Metier lvl 6 section 
create_section6 <- function(met6, CEAREA6, CLAREA6) {

   # Header
  pandoc.header(met6, level = 4)
  
  pandoc.p("This section presents a description of the main species landed in weight and value for the metiers at level 6. The top 15 and all the other species grouped (‘Other’) are displayed in the first two figures below. The distribution of fishing effort (fishing days and number of trips) by flag country, vessel size length and by quarter are also shown. At the end of this section, there is displayed a map with the spatial distribution of the fishing days by ICES statistical rectangle.")
  
  CLAREA6 <- filter(CLAREA6, CLmetier6 %in% met6)
  CEAREA6 <- filter(CEAREA6, CEmetier6 %in% met6)
  
  
  # Section contents
  ## CL - top 15 species
  
  CLtop15 <- CLAREA6 %>%
    group_by(Description) %>%
    summarise(ToTw = sum(CLscientificWeight, na.rm = TRUE)) %>%
    top_n(15, ToTw ) %>%
    mutate(x = "x")
  
  CLtopSp <- left_join(CLAREA6, CLtop15, by = "Description") %>%
    mutate(Description = ifelse(is.na(x), "Others", Description))
  ### Weight
  w <- CLtopSp %>%
    group_by(Description) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE)) %>%
    ggplot(aes(reorder(Description, -CLscientificWeight), CLscientificWeight)) +
    geom_bar(stat = "identity")    +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(text = element_text(size = 15)) +
    xlab("Scientific name") +
    ylab("Weight (t)") +
    ggtitle(paste0("Landed weight (t) top 15 species (", met6,")"))
  print(w)
  
  ### Value 
  l <- CLtopSp %>%
    group_by(Description) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    ggplot(aes(reorder(Description, -CLlandingsValue), CLlandingsValue)) +
    geom_bar(stat = "identity")    +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(text = element_text(size = 15)) +
    xlab("Scientific name")+
    ylab("Value in €") +
    ggtitle(paste0("Landed value (€) top 15 species (", met6 ,")"))
  print(l)
  
  ## CE 
  ### Flag country 
  f <- CEAREA6 %>%
    group_by(CEvesselFlagCountry) %>%
    summarise(CEscientificDaysAtSea = sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
    ggplot(aes(reorder(CEvesselFlagCountry, -CEscientificDaysAtSea), CEscientificDaysAtSea)) +
    geom_bar(stat = "identity")    +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(text = element_text(size = 15)) +
    xlab("Flag Country")+
    ggtitle(paste0("Fishing days by flag country (", met6, ")")) 
  print(f)
  
  
  t <- CEAREA6 %>%
    group_by(CEvesselFlagCountry) %>%
    summarise(CEnumberOfFractionalTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    ggplot(aes(reorder(CEvesselFlagCountry, -CEnumberOfFractionalTrips), CEnumberOfFractionalTrips)) +
    geom_bar(stat = "identity")    +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(text = element_text(size = 15)) +
    xlab("Flag Country")+
    ggtitle(paste0("Number of trips by flag country (", met6,")"))
  print(t)
  ### Vessel length 
  
   v1 <- CEAREA6 %>%
    group_by(CEvesLenCat) %>%
    summarise(CEscientificDaysAtSea = sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
    ggplot(aes(CEvesLenCat, CEscientificDaysAtSea)) +
    geom_bar(stat = "identity")    +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(text = element_text(size = 15)) +
    xlab("Vessel Length")+
    ggtitle(paste0("Fishing days by vessel length group (", met6 ,")"))
  print(v1)
  
  v2 <- CEAREA6 %>%
    group_by(CEvesLenCat) %>%
    summarise(CEnumberOfFractionalTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    ggplot(aes( CEvesLenCat, CEnumberOfFractionalTrips)) +
    geom_bar(stat = "identity")    +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(text = element_text(size = 15)) +
    xlab("Vessel Length")+
    ggtitle(paste0("Number of trips by vessel length group (", met6, ")"))
  print(v2)
  
  ### Quarter
    q1 <- CEAREA6 %>%
    group_by(CEquarter) %>%
    summarise(CEscientificDaysAtSea = sum(CEscientificDaysAtSea, na.rm = TRUE)) %>%
    ggplot(aes( CEquarter, CEscientificDaysAtSea)) +
    geom_bar(stat = "identity")    +
    theme(text = element_text(size = 15)) +
    xlab("Quarter")+
    ggtitle(paste0("Fishing days by quarter (", met6 ,")"))
  print(q1)
  
   q2 <- CEAREA6 %>%
    group_by(CEquarter) %>%
    summarise(CEnumberOfFractionalTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    ggplot(aes( CEquarter, CEnumberOfFractionalTrips)) +
    geom_bar(stat = "identity")    +
    theme(text = element_text(size = 15)) +
    xlab("Quarter")+
    ggtitle(paste0("Number of trips by quarter (", met6 ,")"))
  print(q2)
  
  
  ### Map - Fishing days 
  mapDat <- CEAREA6 %>%
    group_by(CEstatisticalRectangle) %>%
    summarise(CEscientificDaysAtSea = sum(CEscientificDaysAtSea, na.rm = TRUE))
  
  
  mapdata <- left_join(rect, mapDat, by = c("ICESNAME" = "CEstatisticalRectangle" )) %>%  filter(!is.na(CEscientificDaysAtSea))
  
  
  
  #Setting lim
  ylim_min <- min(mapdata$SOUTH, na.rm = T)
  ylim_max <- max(mapdata$NORTH, na.rm = T)
  xlim_min <- min(mapdata$WEST, na.rm = T)
  xlim_max <- max(mapdata$EAST, na.rm = T)
  xlim <- c(xlim_min - 2, xlim_max + 2)
  ylim <- c(ylim_min - 1, ylim_max + 1)
  
  mm <- ggplot() + 
    geom_sf(data = rect) +
    geom_sf(data = mapdata, aes(fill = CEscientificDaysAtSea)) +
    geom_sf(data = world) +
    coord_sf(xlim = xlim, ylim = ylim, expand = FALSE) +
    xlab("Longitude") +
    ylab("Latitude")+
    scale_fill_gradient(low="lightblue", high="red") +
    ggtitle("Fishing days by ICES rectangle")   +
    theme(text = element_text(size = 15)) 
  
  print(mm)
  
  # empty lines to be sure that this is valid Markdown
  pandoc.p('')
  
   }

```



```{r, results='asis'}

#initialize
create_section4(CEtop6$CEmetier4[1], CEAREA, CLAREA)
create_section5(CEtop6$CEmetier5[1], CEAREA4, CLAREA4)
create_section6(CEtop6$CEmetier6[1], CEAREA6, CLAREA6)
#loop
for (i in 2:nrow(CEtop6)) {
  if(CEtop6$CEmetier4[i-1] != CEtop6$CEmetier4[i]){
    create_section4(CEtop6$CEmetier4[i], CEAREA, CLAREA)
  }
  if(CEtop6$CEmetier5[i-1] != CEtop6$CEmetier5[i]){
    create_section5(CEtop6$CEmetier5[i], CEAREA4, CLAREA4)
  }
    if(CEtop6$CEmetier6[i-1] != CEtop6$CEmetier6[i]){
    create_section6(CEtop6$CEmetier6[i], CEAREA6, CLAREA6)
    cat(" \n")
  }

}
```




