---
author: "ISSG Metier Overviews"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    smoothScrollSpeed: "fast"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile,
  encoding = encoding, 
  output_file = file.path(dirname(inputFile), "NAtl_2023.html"))}) # <--- Change region here; Change year here (2021;2022;2023)
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.dim = c(14, 10)
)
options(scipen = 999)
options(error = traceback)
options(error = recover)
knitr::opts_knit$set(root.dir = "H:/c-users/RDBES/CE_CL_2025")  # <----- add working directory
```

```{r}
library(tidyverse, quietly=TRUE, warn.conflicts=FALSE)
library(knitr)
library(ggplot2)
library(cowplot)
library(pander)
library(ggpubr)
library(kableExtra)
library(sf)
library(rnaturalearth)
library(RColorBrewer)
library(data.table)
```

```{r}
# Set RCG region - NSEA, NAtl, BALT
rr <- "NAtl" # <---------- and here 
year <- 2023 # <---------- change year here

if(rr %in% "NSEA"){
  title <- paste("North Sea and Eastern Arctic -", year)
}else if(rr %in% "NAtl"){
  title <- paste("North Atlantic -", year)
}else{
  title <- paste("Baltic -", year)
}

```

---
title: "`r title`"
---


```{r}
# Reference lists 
## Scientific name 
urls <- "https://raw.githubusercontent.com/ices-eg/RCGs/master/Metiers/Scripts/ICESVocabSpecies/ICESVocabAphiaIDScienName_2023.csv"
ScienName <- read.csv(urls, header = TRUE)

### Remove deprecated and invalid records 
ScienName <- filter(ScienName, !Deprecated %in% c("", "True", "2020-09-16")) %>%
  select(Code, Description) %>%
  mutate(Code = as.numeric(Code))
## Area - region (normal path gives back xml version)
url <- "https://raw.githubusercontent.com/ices-eg/RCGs/master/Metiers/Reference_lists/AreaRegionLookup.csv"
Area <- read.csv(url, header = TRUE)
### Fix the extra space in rcg region code
Area <- mutate(Area, Code = ifelse(Code %in% "NSEA                                    " , "NSEA",
                             ifelse(Code %in% "NAtl                                      ", "NAtl", Code))) %>%
  select(AreaCode, Code)

### Shapefiles 
### Need to source it from online - Can't open it
# rect <- read_sf("https://raw.githubusercontent.com/ices-eg/RCGs/Metiers/Scripts/RectangleShapefiles/StatRec_map_Areas_Full_20170124.shp")

#rect <- read_sf("C:/Users/molla004/OneDrive - Wageningen University & #Research/Git/hub/RCGs/Metiers/Scripts/RectangleShapefiles/StatRec_map_Areas_Full_20170124.shp")

rect <- read_sf("H:/c-users/RDBES/MetierReports/RectangleShapefiles/StatRec_map_Areas_Full_20170124.shp")
world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

# ---------------------------
# Confidentiality parameters
# ---------------------------
vessel_limit <- 3

# Count vessels
count_vessels <- function(data, group_vars, vessel_id,
                           sep = "\\s*;\\s*|\\s*/\\s*") {
  data %>%
    tidyr::separate_rows({{ vessel_id }}, sep = sep) %>%
    dplyr::group_by(across({{ group_vars }})) %>%
    summarise(
      n_vessels = n_distinct({{ vessel_id }}),
      .groups = "drop"
    )
}


compute_removed_pct <- function(data,
                                group_vars,
                                value_var,
                                vessel_id,
                                vessel_limit = 3) {

  total_before <- data %>%
    summarise(
      total = suppressWarnings(
        sum(as.numeric({{ value_var }}), na.rm = TRUE)
      )
    ) %>%
    pull(total)

  if (is.na(total_before) || total_before == 0) return(0)

  total_after <- data %>%
    left_join(
      count_vessels(
        data,
        group_vars = {{ group_vars }},
        vessel_id  = {{ vessel_id }}
      ),
      by = dplyr::group_vars(
        dplyr::group_by(data, across({{ group_vars }}))
      )
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    summarise(
      total = suppressWarnings(
        sum(as.numeric({{ value_var }}), na.rm = TRUE)
      )
    ) %>%
    pull(total)

  round(100 * (total_before - total_after) / total_before, 1)
}



print_removed_table <- function(x, caption) {

  html <- paste0(
    "<p><strong>", caption, "</strong></p>",
    knitr::kable(
      x,
      format = "html",
      digits = 1
    ) |>
      kableExtra::kable_styling(
        full_width = FALSE,
        position = "left"
      )
  )

  cat(html)
}


```

```{r}
# Read data 

CL <- fread("H:/RDBES/2026/HCL_NANSEA_2021_2026/CommercialLanding.csv", quote = "")  
CE <- fread("H:/RDBES/2026/HCE_NANSEA/CommercialEffort.csv", quote="")

# Filter year (2021, 2022, 2023)
CL <- subset(CL, CLyear == "2023") # <---------- change year here
CE <- subset(CE, CEyear == "2023") # <---------- change year here

```

```{r}
# Select only area 27 
CL <- filter(CL, substr(CLarea, 1, 2) %in% "27")
CE <- filter(CE, substr(CEarea, 1, 2) %in% "27")

# Assign regions (and split? Need to do this at the end of processing then)
CL <- left_join(CL, Area, by = c("CLarea" = "AreaCode"))
#table(CL$Code, useNA = "always") # 6 NAs from area 27 (IE, GB) - exclude for now, check!!!  
                                  # 5 NAS 2021; 1 NA 2022; 13 NAS 2023
CL <- filter(CL, !is.na(Code))

CE <- left_join(CE, Area, by = c("CEarea" = "AreaCode"))
#table(CE$Code, useNA = "always") # No NA's
```

```{r}
# Merge for scientific name 
CL <- left_join(CL, ScienName, by = c("CLspeciesCode" = "Code"))
```


```{r}
# Process

## Year string 
CL$CLyear <- as.character(CL$CLyear)
CE$CEyear <- as.character(CE$CEyear)

## Month factors 
CL$CLmonth <- factor(CL$CLmonth, levels = as.character(c(1:12)))
CE$CEmonth <- factor(CE$CEmonth, levels = as.character(c(1:12)))

## Quarter factors 
CL$CLquarter <- factor(CL$CLquarter, levels = as.character(c(1:4)))
CE$CEquarter <- factor(CE$CEquarter, levels = as.character(c(1:4)))

## Vessel length factors 
CL$CLvesLenCat <- factor(CL$CLvesselLengthCategory, levels = c("VL0006","VL0608", "VL0810", "VL1012", "VL1215", "VL1518", "VL1824", "VL2440", "VL40XX", "NK"))
CE$CEvesLenCat <- factor(CE$CEvesselLengthCategory, levels = c("VL0006","VL0608", "VL0810", "VL1012", "VL1215", "VL1518", "VL1824", "VL2440", "VL40XX", "NK"))

## Country factors 
CL$CLvesselFlagCountry <- factor(CL$CLvesselFlagCountry, levels = sort(unique(CL$CLvesselFlagCountry)))
CE$CEvesselFlagCountry <- factor(CE$CEvesselFlagCountry, levels = sort(unique(CE$CEvesselFlagCountry)))


## Get metier lvl 4 
CL <- mutate(CL, CLmetier4 = str_extract(CLmetier6, "[^_]+"))
CE <- mutate(CE, CEmetier4 = str_extract(CEmetier6, "[^_]+"))

## Get metier lvl 5 
CL <- mutate(CL, CLmetier5 = str_extract(CLmetier6,  "[^_]*_[^_]*"))
CE <- mutate(CE, CEmetier5 = str_extract(CEmetier6,  "[^_]*_[^_]*"))


# Weight kg to t 
CL <- mutate(CL, CLscientificWeight = round(CLscientificWeight/1000, digits = 2))

# Filter CatchCategory == Landings
CL <- filter(CL, CLcatchCategory %in% "Lan")

```


```{r}
# Filter by area 
CLAREA <- filter(CL, Code %in% rr)

CEAREA <- filter(CE, Code %in% rr)

```


```{r}
# Set country colors
ct.cols <- 14 
myColors <- colorRampPalette(brewer.pal(8, "Set2"))(ct.cols)
names(myColors) <- levels(CL$CLvesselFlagCountry)
colScale <- scale_fill_manual(name = "CLvesselFlagCountry",values = myColors)

```


```{r}
# Top 10 metiers by region based on FISHING DAYS 
# Select top 10 lvl 4 
# Select top 10 metier lvl 5 from the top 10 metier lvl 4
# Select top 5 metier lvl 6 from the top 10 metier lvl 5 
#--- Keep all metier lvl 5 and metier lvl 6 for the respective summary plots  

# TODO - more than 5% of total fishing days and less than 10/5

# Lvl 4 

CEtop4 <- CEAREA %>%
  group_by(CEmetier4) %>%
  summarise(Fd = sum(CEscientificFishingDays, na.rm = TRUE)) %>%
  mutate(ToTfd = sum(Fd),
         Perc = (Fd/ToTfd)*100)%>%
  top_n(10, Perc)

CEAREA4 <- filter(CEAREA, CEmetier4 %in% unique(CEtop4$CEmetier4))

# Lvl 5 
CEtop5 <- CEAREA4 %>%
  group_by(CEmetier4, CEmetier5) %>%
  summarise(Fd = sum(CEscientificFishingDays, na.rm = TRUE))  %>%
  mutate(ToTfd = sum(Fd),
         Perc = (Fd/ToTfd)*100) %>%
  filter(Perc > 5)

CEAREA5 <- filter(CEAREA4, CEmetier5 %in% unique(CEtop5$CEmetier5))


# Lvl 6 - top 5
CEtop6 <- CEAREA5 %>%
  group_by(CEmetier4, CEmetier5, CEmetier6) %>%
  summarise(Fd = sum(CEscientificFishingDays, na.rm = TRUE)) %>%
  mutate(ToTfd = sum(Fd),
         Perc = (Fd/ToTfd)*100) %>%
  filter(Perc > 5)

# Arrange based on index mesh size
CEtop6$mesh1 <- sapply(str_split(CEtop6$CEmetier6, fixed("_")), "[", 3)
CEtop6$mesha <- as.numeric(sapply(str_extract_all(CEtop6$mesh1, "\\d+"), "[", 1))
CEtop6 <- mutate(CEtop6, mesha = as.numeric(mesha))
CEtop6 <- CEtop6 %>%
  arrange(CEmetier4, CEmetier5, mesha)


# Lvl 6 
CEAREA6 <- filter(CEAREA5, CEmetier6 %in% unique(CEtop6$CEmetier6))
CLAREA4 <- filter(CLAREA, CLmetier4 %in% unique(CEtop4$CEmetier4))
CLAREA5 <- filter(CLAREA4, CLmetier5 %in% unique(CEtop5$CEmetier5))
CLAREA6 <- filter(CLAREA5, CLmetier6 %in% unique(CEtop6$CEmetier6))
```


# Summary 

This report presents the description of the main metiers in the `r title`. The data used to produce the report is from the ‘Commercial Landings’ (CL) and ‘Commercial Effort’ (CE) tables submitted to the RDBES in 2026. The description of the metiers includes information on scientific landings (weight and value) and scientific effort (number of fishing days and number of trips), by country, metier and vessel size range. The CL information presented in this report refers only to the catch category for the landings (‘Lan’), ignoring the other possible options (e.g. ‘BMS’ and ‘RegDis’). The information is displayed in an hierarchical mode, from the lowest (level 4) to the highest (level 6) metier. The top 10 metiers at level 4 are selected according to the scientific effort in number of fishing days. The metiers at levels 5 and 6 presented in this report are the ones that have more than 5% of the total fishing days within the previous metier level. It is important to note that if scientific landing weight was considered for selecting the main metiers (instead of the effort), probably other important metiers might also be included in these descriptions.

**Update in 2026: All tables and graphs have been filtered so that it only shows data where there are at least 3 vessels. In connection to plots and tables, a supplementary table indicates the percentage of data removed due to appliation of confidentiality rules.**


# All metier level 4 

The landings and effort overview of all metiers at level 4 present in the North Atlantic are displayed in the set of figures below.



```{r, results='asis'}
  
## -----------------------------------------
## Table: totals by métier level 4
## -----------------------------------------

# CL totals
tab_cl <- CLAREA %>%
  group_by(CLmetier4) %>%
  summarise(
    ScientificWeight = sum(CLscientificWeight, na.rm = TRUE),
    Value = sum(as.numeric(CLlandingsValue), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  rename(Metier4 = CLmetier4)

# CE totals
tab_ce <- CEAREA %>%
  group_by(CEmetier4) %>%
  summarise(
    ScientificFishingDays = sum(CEscientificFishingDays, na.rm = TRUE),
    NumberOfTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  rename(Metier4 = CEmetier4)

# Vessel counts (authoritative source)
ce_v_metier <- count_vessels(
  data = CEAREA,
  group_vars = CEmetier4,
  vessel_id  = CEencryptedVesselIds
) %>%
  rename(Metier4 = CEmetier4)

# Merge and apply confidentiality rule
final_table <- tab_cl %>%
  left_join(tab_ce, by = "Metier4") %>%
  left_join(ce_v_metier, by = "Metier4") %>%
  filter(n_vessels >= vessel_limit) %>%
  select(-n_vessels)

# Print main table
final_table %>%
  kbl(caption = "Total values by métier level 4") %>%
  kable_styling()

removed_m4_table <- tibble(
  ScientificWeight =compute_removed_pct(CLAREA,group_vars = CLmetier4,value_var  = CLscientificWeight,vessel_id  = CLencryptedVesselIds),
  Value =compute_removed_pct(CLAREA,group_vars = CLmetier4,value_var  = CLlandingsValue,vessel_id  = CLencryptedVesselIds),
  ScientificFishingDays =compute_removed_pct(CEAREA,group_vars = CEmetier4,value_var  = CEscientificFishingDays,vessel_id  = CEencryptedVesselIds),
  NumberOfTrips =compute_removed_pct(CEAREA,group_vars = CEmetier4,value_var  = CEnumberOfFractionalTrips,vessel_id  = CEencryptedVesselIds)
)

print_removed_table(
  removed_m4_table,
  "Percentage of data removed in the table above due to confidentiality rule (n < 3)"
)


```

---


```{r, results='asis'}

  p1 <- CLAREA %>%
    left_join(
      count_vessels(CLAREA,group_vars = c(CLmetier4, CLvesselFlagCountry),vessel_id = CLencryptedVesselIds),
      by = c("CLmetier4","CLvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CLmetier4, CLvesselFlagCountry) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE)) %>%
    group_by(CLmetier4) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot( aes(reorder(CLmetier4, -TotW), CLscientificWeight, fill = CLvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    colScale +
    xlab("Metier lvl 4") +
    ylab("Weight (t)") +    
    ggtitle("Landed weight (t) by country and metier level 4") 
  
  p2 <- CLAREA %>%
    left_join(
      count_vessels(CLAREA,group_vars = c(CLmetier4, CLvesselFlagCountry),vessel_id = CLencryptedVesselIds),
      by = c("CLmetier4","CLvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CLmetier4, CLvesselFlagCountry) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    group_by(CLmetier4) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot( aes(x= reorder(CLmetier4, -TotL), y=CLlandingsValue, fill =  CLvesselFlagCountry)) +     
    geom_bar(stat = "identity") +
    xlab("Metier lvl 4") +
    ylab("Value in €") +
    ggtitle("Landed value (€) by country and metier level 4") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    colScale 
  
  # CE 
  
  k1 <- CEAREA %>%
    left_join(
      count_vessels(CEAREA,group_vars = c(CEmetier4, CEvesselFlagCountry),vessel_id = CEencryptedVesselIds),
      by = c("CEmetier4","CEvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEmetier4, CEvesselFlagCountry) %>%
    summarise(CEscientificFishingDays= sum(CEscientificFishingDays, na.rm = TRUE)) %>%
    group_by(CEmetier4) %>%
    mutate(TotD = sum(CEscientificFishingDays)) %>%
    ggplot( aes(reorder(CEmetier4, -TotD),CEscientificFishingDays, fill = CEvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 4") +
    ylab("Scientific fishing days") +
    ggtitle("Fishing days by country and metier level 4")  +
    colScale
  
  k2 <- CEAREA %>%
    left_join(
      count_vessels(CEAREA,group_vars = c(CEmetier4, CEvesselFlagCountry),vessel_id = CEencryptedVesselIds),
      by = c("CEmetier4","CEvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEmetier4, CEvesselFlagCountry) %>%
    summarise(CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    group_by(CEmetier4) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>% 
    ggplot( aes(reorder(CEmetier4, -TotD),CEnumberOfFractionalTrips, fill = CEvesselFlagCountry)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    xlab("Metier lvl 4") +
    ylab("Number of trips") +
    ggtitle("Number of trips by country and metier level 4")  +
    colScale
  
  l <- ggarrange(p1, p2, k1, k2, ncol = 2, nrow = 2)
  print(l)
  
    removed_country_m4 <- tibble(
      ScientificWeight = compute_removed_pct(CLAREA,c(CLmetier4, CLvesselFlagCountry),CLscientificWeight,CLencryptedVesselIds),
      Value = compute_removed_pct(CLAREA,c(CLmetier4, CLvesselFlagCountry),CLlandingsValue,CLencryptedVesselIds),
      ScientificFishingDays =compute_removed_pct(CEAREA,c(CEmetier4, CEvesselFlagCountry),CEscientificFishingDays,CEencryptedVesselIds),
      NumberOfTrips =compute_removed_pct(CEAREA,c(CEmetier4, CEvesselFlagCountry),CEnumberOfFractionalTrips,CEencryptedVesselIds)
    )
    
  print_removed_table(removed_country_m4,"Percentage of data removed in the plots above due to confidentiality rule (n < 3) – métier level 4 by country")

  # Vessel length category 
  vl1 <- CLAREA %>%
    left_join(
      count_vessels(CLAREA,group_vars = c(CLmetier4, CLvesLenCat),vessel_id = CLencryptedVesselIds),
      by = c("CLmetier4","CLvesLenCat")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CLmetier4, CLvesLenCat) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE)) %>%
    group_by(CLmetier4) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot( aes(reorder(CLmetier4, -TotW), CLscientificWeight, fill = CLvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 4") +
    ylab("Weight (t)") +
    ggtitle("Landed weight (t) by vessel length category and metier level 4") 
  
  vl2 <- CLAREA %>%
    left_join(
      count_vessels(CLAREA,group_vars = c(CLmetier4, CLvesLenCat),vessel_id = CLencryptedVesselIds),
      by = c("CLmetier4","CLvesLenCat")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CLmetier4, CLvesLenCat) %>%
    summarise(CLlandingsValue= sum(as.numeric(CLlandingsValue), na.rm = TRUE)) %>%
    group_by(CLmetier4) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot( aes(x= reorder(CLmetier4, -TotL), y=CLlandingsValue, fill =  CLvesLenCat)) +     
    geom_bar(stat = "identity") +
    xlab("Metier lvl 4") +
    ylab("Value in €") +
    ggtitle("Landed value (€) by vessel length category and metier level 4") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
  
  # CE 
  vl3 <- CEAREA %>%
    left_join(
      count_vessels(CEAREA,group_vars = c(CEmetier4, CEvesLenCat),vessel_id = CEencryptedVesselIds),
      by = c("CEmetier4","CEvesLenCat")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEmetier4, CEvesLenCat) %>%
    summarise(CEscientificFishingDays= sum(CEscientificFishingDays, na.rm = TRUE)) %>%
    group_by(CEmetier4) %>%
    mutate(TotD = sum(CEscientificFishingDays)) %>%
    ggplot( aes(reorder(CEmetier4, -TotD),CEscientificFishingDays, fill = CEvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("Metier lvl 4") +
    ggtitle("Fishing days by vessel length category and metier level 4")  
  
  vl4 <- CEAREA %>%
    left_join(
      count_vessels(CEAREA,group_vars = c(CEmetier4, CEvesLenCat),vessel_id = CEencryptedVesselIds),
      by = c("CEmetier4","CEvesLenCat")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEmetier4, CEvesLenCat) %>%
    summarise(CEnumberOfFractionalTrips= sum(CEnumberOfFractionalTrips, na.rm = TRUE)) %>%
    group_by(CEmetier4) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>% 
    ggplot( aes(reorder(CEmetier4, -TotD),CEnumberOfFractionalTrips, fill = CEvesLenCat)) +
    geom_bar(stat = "identity") + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  +
    xlab("Metier lvl 4") +
    ggtitle("Number of trips by vessel length category and metier level 4")  
  
  vlf <- ggarrange(vl1, vl2, vl3, vl4, ncol = 2, nrow = 2)
  print(vlf)
  
  removed_length <- tibble::tibble(
  ScientificWeight =compute_removed_pct(CLAREA,group_vars = c(CLmetier4, CLvesLenCat),value_var  = CLscientificWeight,vessel_id  = CLencryptedVesselIds, vessel_limit = vessel_limit),
  Value =compute_removed_pct(CLAREA,group_vars = c(CLmetier4, CLvesLenCat),value_var  = CLlandingsValue,vessel_id  = CLencryptedVesselIds,vessel_limit = vessel_limit),
  ScientificFishingDays =compute_removed_pct(CEAREA,group_vars = c(CEmetier4, CEvesLenCat),value_var  = CEscientificFishingDays,vessel_id  = CEencryptedVesselIds, vessel_limit = vessel_limit),
  NumberOfTrips =compute_removed_pct(CEAREA,group_vars = c(CEmetier4, CEvesLenCat),value_var  = CEnumberOfFractionalTrips,vessel_id  = CEencryptedVesselIds, vessel_limit = vessel_limit)
    )

print_removed_table(removed_length,"Percentage of data removed in the plots above due to confidentiality rule (n < 3) – métier level 4 by vessel length category")

```

---

# Top 10 metier level 4 


```{r, results='asis'}
create_section4 <- function(met4, CEAREA, CLAREA) {

  
  if (is.null(met4) || length(met4) == 0 || is.na(met4)) {
      return(invisible(NULL))
    }

  # Header
  pander::pandoc.header(met4, level = 2)

  # -----------------------------
  # Plots: by country (metier 5)
  # -----------------------------

  p1 <- CLAREA %>%
    left_join(
      count_vessels(CLAREA,
                     group_vars = c(CLmetier5, CLvesselFlagCountry),
                     vessel_id = CLencryptedVesselIds),
      by = c("CLmetier5","CLvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit, CLmetier4 %in% met4) %>%
    group_by(CLmetier5, CLvesselFlagCountry) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE),
              .groups = "drop") %>%
    group_by(CLmetier5) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot(aes(reorder(CLmetier5, -TotW),
               CLscientificWeight,
               fill = CLvesselFlagCountry)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Metier level 5",
      y = "Weight (t)",
      title = paste0("Landed weight (t) by country (", met4, ")")
    ) +
    colScale

  p2 <- CLAREA %>%
    left_join(
      count_vessels(CLAREA,
                     group_vars = c(CLmetier5, CLvesselFlagCountry),
                     vessel_id = CLencryptedVesselIds),
      by = c("CLmetier5","CLvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit, CLmetier4 %in% met4) %>%
    group_by(CLmetier5, CLvesselFlagCountry) %>%
    summarise(CLlandingsValue = sum(as.numeric(CLlandingsValue), na.rm = TRUE),
              .groups = "drop") %>%
    group_by(CLmetier5) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot(aes(reorder(CLmetier5, -TotL),
               CLlandingsValue,
               fill = CLvesselFlagCountry)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Metier level 5",
      y = "Value (€)",
      title = paste0("Landed value (€) by country (", met4, ")")
    ) +
    colScale

  k1 <- CEAREA %>%
    left_join(
      count_vessels(CEAREA,
                     group_vars = c(CEmetier5, CEvesselFlagCountry),
                     vessel_id = CEencryptedVesselIds),
      by = c("CEmetier5","CEvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit, CEmetier4 %in% met4) %>%
    group_by(CEmetier5, CEvesselFlagCountry) %>%
    summarise(CEscientificFishingDays = sum(CEscientificFishingDays, na.rm = TRUE),
              .groups = "drop") %>%
    group_by(CEmetier5) %>%
    mutate(TotD = sum(CEscientificFishingDays)) %>%
    ggplot(aes(reorder(CEmetier5, -TotD),
               CEscientificFishingDays,
               fill = CEvesselFlagCountry)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Metier level 5",
      y = "Fishing days",
      title = paste0("Fishing days by country (", met4, ")")
    ) +
    colScale

  k2 <- CEAREA %>%
    left_join(
      count_vessels(CEAREA,
                     group_vars = c(CEmetier5, CEvesselFlagCountry),
                     vessel_id = CEencryptedVesselIds),
      by = c("CEmetier5","CEvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit, CEmetier4 %in% met4) %>%
    group_by(CEmetier5, CEvesselFlagCountry) %>%
    summarise(CEnumberOfFractionalTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE),
              .groups = "drop") %>%
    group_by(CEmetier5) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>%
    ggplot(aes(reorder(CEmetier5, -TotD),
               CEnumberOfFractionalTrips,
               fill = CEvesselFlagCountry)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Metier level 5",
      y = "Number of trips",
      title = paste0("Number of trips by country (", met4, ")")
    ) +
    colScale

  l <- ggarrange(p1, p2, k1, k2, ncol = 2, nrow = 2)
  print(l)

  # -----------------------------
  # % removed table (by country)
  # -----------------------------

  removed_country_m5 <- tibble(
    ScientificWeight =compute_removed_pct(CLAREA %>% filter(CLmetier4 %in% met4),group_vars = c(CLmetier5, CLvesselFlagCountry),value_var  = CLscientificWeight,
        vessel_id  = CLencryptedVesselIds),
    Value =compute_removed_pct(CLAREA %>% filter(CLmetier4 %in% met4),group_vars = c(CLmetier5, CLvesselFlagCountry),value_var  = CLlandingsValue,vessel_id  = CLencryptedVesselIds),
    ScientificFishingDays =compute_removed_pct(CEAREA %>% filter(CEmetier4 %in% met4),group_vars = c(CEmetier5, CEvesselFlagCountry),value_var  = CEscientificFishingDays, vessel_id  = CEencryptedVesselIds),
    NumberOfTrips =compute_removed_pct(CEAREA %>% filter(CEmetier4 %in% met4),group_vars = c(CEmetier5, CEvesselFlagCountry),value_var  = CEnumberOfFractionalTrips,vessel_id  = CEencryptedVesselIds))

  
print_removed_table(removed_country_m5, paste0("Percentage of data removed in the figures above due to confidentiality rule (n < 3) – métier level 5 (", met4, ")"))

  pander::pandoc.p("")
}

```

---

```{r, results='asis'}

create_section5 <- function(met5, CEAREA4, CLAREA4) {

  
  if (is.null(met5) || length(met5) == 0 || is.na(met5)) {
      return(invisible(NULL))
    }

  # Header
  pander::pandoc.header(met5, level = 3)
  pandoc.p("Summary table with information on the scientific landings and fishing effort of all métiers at level 5, by flag country.")

  CLAREA4 <- filter(CLAREA4, CLmetier5 %in% met5)
  CEAREA4 <- filter(CEAREA4, CEmetier5 %in% met5)

  # ---------------------------------
  # Table: totals by country (M5)
  # ---------------------------------
  tab1 <- CLAREA4 %>%
    left_join(
      count_vessels(CLAREA4,
                     group_vars = c(CLmetier5, CLvesselFlagCountry),
                     vessel_id = CLencryptedVesselIds),
      by = c("CLmetier5","CLvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CLmetier5, CLvesselFlagCountry) %>%
    summarise(
      ScientificWeight = sum(CLscientificWeight, na.rm = TRUE),
      Value = sum(as.numeric(CLlandingsValue), na.rm = TRUE),
      .groups = "drop"
    ) %>%
    rename(Metier5 = CLmetier5,
           VesselFlagCountry = CLvesselFlagCountry)

  tab2 <- CEAREA4 %>%
    left_join(
      count_vessels(CEAREA4,
                     group_vars = c(CEmetier5, CEvesselFlagCountry),
                     vessel_id = CEencryptedVesselIds),
      by = c("CEmetier5","CEvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEmetier5, CEvesselFlagCountry) %>%
    summarise(
      ScientificFishingDays = sum(CEscientificFishingDays, na.rm = TRUE),
      NumberOfTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    rename(Metier5 = CEmetier5,VesselFlagCountry = CEvesselFlagCountry)

  print(left_join(tab1, tab2) %>%kbl(caption = "Total values by country and métier level 5") %>%kable_styling())

    
  removed_m5_table <- tibble(
    ScientificWeight =compute_removed_pct(CLAREA4,group_vars = c(CLmetier5, CLvesselFlagCountry),value_var  = CLscientificWeight,vessel_id  = CLencryptedVesselIds),
    Value =compute_removed_pct(CLAREA4,group_vars = c(CLmetier5, CLvesselFlagCountry),value_var  = CLlandingsValue,vessel_id  = CLencryptedVesselIds),
    ScientificFishingDays =compute_removed_pct(CEAREA4,group_vars = c(CEmetier5, CEvesselFlagCountry),value_var  = CEscientificDaysAtSea,vessel_id  = CEencryptedVesselIds),
    NumberOfTrips =compute_removed_pct(CEAREA4,group_vars = c(CEmetier5, CEvesselFlagCountry),value_var  = CEnumberOfFractionalTrips,vessel_id  = CEencryptedVesselIds))
  
  print_removed_table(
    removed_m5_table,paste0("Percentage of data removed in the table above due to confidentiality rule (n < 3) – ",
      "métier level 5 (", met5, ")"))

  # ---------------------------------
  # Plots: M6 by country
  # ---------------------------------
  p1 <- CLAREA4 %>%
    left_join(
      count_vessels(CLAREA4,
                     group_vars = c(CLmetier6, CLvesselFlagCountry),
                     vessel_id = CLencryptedVesselIds),
      by = c("CLmetier6","CLvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CLmetier6, CLvesselFlagCountry) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE),
              .groups = "drop") %>%
    group_by(CLmetier6) %>%
    mutate(TotW = sum(CLscientificWeight)) %>%
    ggplot(aes(reorder(CLmetier6, -TotW),
               CLscientificWeight,
               fill = CLvesselFlagCountry)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(title = paste0("Landed weight (t) by country (", met5, ")"),
         x = "Métier level 6", y = "Weight (t)") +
    colScale

  p2 <- CLAREA4 %>%
    left_join(
      count_vessels(CLAREA4,
                     group_vars = c(CLmetier6, CLvesselFlagCountry),
                     vessel_id = CLencryptedVesselIds),
      by = c("CLmetier6","CLvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CLmetier6, CLvesselFlagCountry) %>%
    summarise(CLlandingsValue = sum(as.numeric(CLlandingsValue), na.rm = TRUE),
              .groups = "drop") %>%
    group_by(CLmetier6) %>%
    mutate(TotL = sum(CLlandingsValue)) %>%
    ggplot(aes(reorder(CLmetier6, -TotL),
               CLlandingsValue,
               fill = CLvesselFlagCountry)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(title = paste0("Landed value (€) by country (", met5, ")"),
         x = "Métier level 6", y = "Value (€)") +
    colScale

  k1 <- CEAREA4 %>%
    left_join(
      count_vessels(CEAREA4,
                     group_vars = c(CEmetier6, CEvesselFlagCountry),
                     vessel_id = CEencryptedVesselIds),
      by = c("CEmetier6","CEvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEmetier6, CEvesselFlagCountry) %>%
    summarise(CEscientificFishingDays= sum(CEscientificFishingDays, na.rm = TRUE),
              .groups = "drop") %>%
    group_by(CEmetier6) %>%
    mutate(TotD = sum(CEscientificFishingDays)) %>%
    ggplot(aes(reorder(CEmetier6, -TotD),
               CEscientificFishingDays,
               fill = CEvesselFlagCountry)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(title = paste0("Fishing days by country (", met5, ")"),
         x = "Métier level 6", y = "Fishing days") +
    colScale

  k2 <- CEAREA4 %>%
    left_join(
      count_vessels(CEAREA4,
                     group_vars = c(CEmetier6, CEvesselFlagCountry),
                     vessel_id = CEencryptedVesselIds),
      by = c("CEmetier6","CEvesselFlagCountry")) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEmetier6, CEvesselFlagCountry) %>%
    summarise(CEnumberOfFractionalTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE),
              .groups = "drop") %>%
    group_by(CEmetier6) %>%
    mutate(TotD = sum(CEnumberOfFractionalTrips)) %>%
    ggplot(aes(reorder(CEmetier6, -TotD),
               CEnumberOfFractionalTrips,
               fill = CEvesselFlagCountry)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(title = paste0("Number of trips by country (", met5, ")"),
         x = "Métier level 6", y = "Number of trips") +
    colScale

  print(ggarrange(p1, p2, k1, k2, ncol = 2, nrow = 2))

  # ---------------------------------
  # % removed table (M6 by country)
  # ---------------------------------
  removed_m6_country <- tibble(
    ScientificWeight =compute_removed_pct(CLAREA4,c(CLmetier6, CLvesselFlagCountry),CLscientificWeight,CLencryptedVesselIds),
    Value =compute_removed_pct(CLAREA4,c(CLmetier6, CLvesselFlagCountry),CLlandingsValue,CLencryptedVesselIds),
    ScientificFishingDays =compute_removed_pct(CEAREA4,c(CEmetier6, CEvesselFlagCountry),CEscientificFishingDays,CEencryptedVesselIds),
    NumberOfTrips =compute_removed_pct(CEAREA4,c(CEmetier6, CEvesselFlagCountry),CEnumberOfFractionalTrips,CEencryptedVesselIds)
  )

  print_removed_table(removed_m6_country, paste0("Percentage of data removed in the figures above due to confidentiality rule (n < 3) – ","métier level 6 by country (", met5, ")"))

  pander::pandoc.p("")
}


```

---

```{r, results='asis'}

create_section6 <- function(met6, CEAREA6, CLAREA6) {

  if (is.null(met6) || length(met6) == 0 || is.na(met6)) {
      return(invisible(NULL))
    }

  # Header
  pandoc.header(met6, level = 4)

  pandoc.p(
    "This section presents a description of the main species landed in weight and value for the métiers at level 6. 
     The top 15 and all other species grouped (‘Others’) are displayed first. 
     Fishing effort is then shown by flag country, vessel length category, quarter, and spatial distribution."
  )

  CLAREA6 <- filter(CLAREA6, CLmetier6 %in% met6)
  CEAREA6 <- filter(CEAREA6, CEmetier6 %in% met6)

  # ---------------------------------
  # CL – Top 15 species
  # ---------------------------------
  CLtop15 <- CLAREA6 %>%
    group_by(Description) %>%
    summarise(ToTw = sum(CLscientificWeight, na.rm = TRUE), .groups = "drop") %>%
    slice_max(ToTw, n = 15) %>%
    mutate(x = "x")

  CLtopSp <- left_join(CLAREA6, CLtop15, by = "Description") %>%
    mutate(Description = ifelse(is.na(x), "Others", Description))

  ## Weight
  w <- CLtopSp %>%
    left_join(
      count_vessels(CLtopSp,
                     group_vars = Description,
                     vessel_id = CLencryptedVesselIds),
      by = "Description"
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(Description) %>%
    summarise(CLscientificWeight = sum(CLscientificWeight, na.rm = TRUE),
              .groups = "drop") %>%
    ggplot(aes(reorder(Description, -CLscientificWeight),
               CLscientificWeight)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Scientific name",
      y = "Weight (t)",
      title = paste0("Landed weight (t) – top 15 species (", met6, ")")
    )

  print(w)

  ## Value
  l <- CLtopSp %>%
    left_join(
      count_vessels(CLtopSp,
                     group_vars = Description,
                     vessel_id = CLencryptedVesselIds),
      by = "Description"
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(Description) %>%
    summarise(CLlandingsValue = sum(as.numeric(CLlandingsValue), na.rm = TRUE),
              .groups = "drop") %>%
    ggplot(aes(reorder(Description, -CLlandingsValue),
               CLlandingsValue)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Scientific name",
      y = "Value (€)",
      title = paste0("Landed value (€) – top 15 species (", met6, ")")
    )

  print(l)

  ## % removed – top 15 species
  removed_m6_top15 <- tibble(
    ScientificWeight =compute_removed_pct(CLtopSp,group_vars = Description,value_var  = CLscientificWeight,vessel_id  = CLencryptedVesselIds),
    Value =compute_removed_pct(CLtopSp,group_vars = Description,value_var  = CLlandingsValue,vessel_id  = CLencryptedVesselIds)
  )

  print_removed_table(removed_m6_top15,paste0("Percentage of data removed due to confidentiality rule (n < 3) – ","top 15 species (", met6, ")"))

  # ---------------------------------
  # CE – Flag country
  # ---------------------------------
  f <- CEAREA6 %>%
    left_join(
      count_vessels(CEAREA6,
                     group_vars = CEvesselFlagCountry,
                     vessel_id = CEencryptedVesselIds),
      by = "CEvesselFlagCountry"
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEvesselFlagCountry) %>%
    summarise(CEscientificFishingDays = sum(CEscientificFishingDays, na.rm = TRUE),
              .groups = "drop") %>%
    ggplot(aes(reorder(CEvesselFlagCountry, -CEscientificFishingDays),
               CEscientificFishingDays)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Flag country",
      y = "Fishing days",
      title = paste0("Fishing days by flag country (", met6, ")")
    )

  print(f)

  t <- CEAREA6 %>%
    left_join(
      count_vessels(CEAREA6,
                     group_vars = CEvesselFlagCountry,
                     vessel_id = CEencryptedVesselIds),
      by = "CEvesselFlagCountry"
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEvesselFlagCountry) %>%
    summarise(CEnumberOfFractionalTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE),
              .groups = "drop") %>%
    ggplot(aes(reorder(CEvesselFlagCountry, -CEnumberOfFractionalTrips),
               CEnumberOfFractionalTrips)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Flag country",
      y = "Number of trips",
      title = paste0("Number of trips by flag country (", met6, ")")
    )

  print(t)

  removed_m6_country <- tibble(
    ScientificFishingDays =compute_removed_pct(CEAREA6,group_vars = CEvesselFlagCountry,value_var  = CEscientificFishingDays,vessel_id  = CEencryptedVesselIds),
    NumberOfTrips =compute_removed_pct(CEAREA6,group_vars = CEvesselFlagCountry,value_var  = CEnumberOfFractionalTrips,vessel_id  = CEencryptedVesselIds) )

  print_removed_table(removed_m6_country,paste0("Percentage of data removed due to confidentiality rule (n < 3) – ",
        "fishing effort by flag country (", met6, ")"))

  
  
  ### Vessel length
  
  v1 <- CEAREA6 %>%
    left_join(
      count_vessels(
        CEAREA6,
        group_vars = CEvesLenCat,
        vessel_id  = CEencryptedVesselIds
      ),
      by = "CEvesLenCat"
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEvesLenCat) %>%
    summarise(
      CEscientificFishingDays = sum(CEscientificFishingDays, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    ggplot(aes(CEvesLenCat, CEscientificFishingDays)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Vessel length category",
      y = "Fishing days",
      title = paste0("Fishing days by vessel length group (", met6, ")")
    )
  
  print(v1)
  
  v2 <- CEAREA6 %>%
    left_join(
      count_vessels(
        CEAREA6,
        group_vars = CEvesLenCat,
        vessel_id  = CEencryptedVesselIds
      ),
      by = "CEvesLenCat"
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEvesLenCat) %>%
    summarise(
      CEnumberOfFractionalTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    ggplot(aes(CEvesLenCat, CEnumberOfFractionalTrips)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(
      x = "Vessel length category",
      y = "Number of trips",
      title = paste0("Number of trips by vessel length group (", met6, ")")
    )
  
  print(v2)
  
  # % removed – vessel length
  removed_m6_length <- tibble(
    ScientificFishingDays =compute_removed_pct(CEAREA6,group_vars = CEvesLenCat,value_var  = CEscientificFishingDays,vessel_id  = CEencryptedVesselIds),
    NumberOfTrips =compute_removed_pct(CEAREA6,group_vars = CEvesLenCat,value_var  = CEnumberOfFractionalTrips,vessel_id  = CEencryptedVesselIds))
  
  print_removed_table(removed_m6_length,paste0("Percentage of data removed due to confidentiality rule (n < 3) – ","fishing effort by vessel length category (", met6, ")"))
  
  
  ### Quarter
  
  q1 <- CEAREA6 %>%
    left_join(
      count_vessels(
        CEAREA6,
        group_vars = CEquarter,
        vessel_id  = CEencryptedVesselIds
      ),
      by = "CEquarter"
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEquarter) %>%
    summarise(
      CEscientificFishingDays = sum(CEscientificFishingDays, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    ggplot(aes(CEquarter, CEscientificFishingDays)) +
    geom_col() +
    labs(
      x = "Quarter",
      y = "Fishing days",
      title = paste0("Fishing days by quarter (", met6, ")")
    )
  
  print(q1)
  
  q2 <- CEAREA6 %>%
    left_join(
      count_vessels(
        CEAREA6,
        group_vars = CEquarter,
        vessel_id  = CEencryptedVesselIds
      ),
      by = "CEquarter"
    ) %>%
    filter(n_vessels >= vessel_limit) %>%
    group_by(CEquarter) %>%
    summarise(
      CEnumberOfFractionalTrips = sum(CEnumberOfFractionalTrips, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    ggplot(aes(CEquarter, CEnumberOfFractionalTrips)) +
    geom_col() +
    labs(
      x = "Quarter",
      y = "Number of trips",
      title = paste0("Number of trips by quarter (", met6, ")")
    )
  
  print(q2)
  
  # % removed – quarter
  removed_m6_quarter <- tibble(
    scientificFishingDays =compute_removed_pct(CEAREA6,group_vars = CEquarter,value_var  = CEscientificFishingDays,vessel_id  = CEencryptedVesselIds),
    NumberOfTrips =compute_removed_pct(CEAREA6,group_vars = CEquarter,value_var  = CEnumberOfFractionalTrips,vessel_id  = CEencryptedVesselIds))
  
  print_removed_table(removed_m6_quarter,paste0("Percentage of data removed due to confidentiality rule (n < 3) – ","fishing effort by quarter (", met6, ")"))
  
   ### Map - Fishing days 
    mapDat <- CEAREA6 %>%
      left_join(
      count_vessels(CEAREA6,group_vars = c(CEstatisticalRectangle),vessel_id = CEencryptedVesselIds),
        by = c("CEstatisticalRectangle")) %>%
      filter(n_vessels >= vessel_limit) %>%
      group_by(CEstatisticalRectangle) %>%
      summarise(CEscientificFishingDays = sum(CEscientificFishingDays, na.rm = TRUE))
    
    
    mapdata <- left_join(rect, mapDat, by = c("ICESNAME" = "CEstatisticalRectangle" )) %>%  filter(!is.na(CEscientificFishingDays))
  

  if (is.null(mapdata) || nrow(mapdata) == 0) {
    message("Skipping plot: no data for this metier")
    return(NULL)
  }

  bb <- sf::st_bbox(mapdata)
  
  if (isTRUE(any(is.na(bb)))) {
    message("Skipping plot: invalid bounding box")
    return(NULL)
  }

  # EXPAND BBOX BY 5% 
  pad <- 0.05
  dx <- (bb["xmax"] - bb["xmin"]) * pad
  dy <- (bb["ymax"] - bb["ymin"]) * pad
  
  bb["xmin"] <- bb["xmin"] - dx
  bb["xmax"] <- bb["xmax"] + dx
  bb["ymin"] <- bb["ymin"] - dy
  bb["ymax"] <- bb["ymax"] + dy
  
  
  rect_crop  <- sf::st_crop(rect,  bb)
  world_crop <- sf::st_crop(world, bb)
  
  mm <- ggplot() +
    geom_sf(data = rect_crop, fill = NA, color = "grey50") +
    geom_sf(data = mapdata, aes(fill = CEscientificFishingDays)) +
    geom_sf(data = world_crop, fill = "grey90", color = "grey70") +
    coord_sf(expand = FALSE) +
    scale_fill_gradient(low = "lightblue", high = "red") +
    labs(
      title = "Fishing days by ICES rectangle",
      x = "Longitude",
      y = "Latitude"
    ) +
    theme(text = element_text(size = 15))
  print(mm)
  
  removed_m6_map <- tibble(ScientificFishingDays =compute_removed_pct(CEAREA6,group_vars = CEstatisticalRectangle,value_var  = CEscientificFishingDays,vessel_id  = CEencryptedVesselIds))
  
  print_removed_table(removed_m6_map,paste0("Percentage of data removed in the map above due to confidentiality rule (n < 3) – ",
        "fishing effort by ICES rectangle (", met6, ")"))
  
    pander::pandoc.p("")
  
}


```



```{r, results='asis'}


if (nrow(CEtop6) == 0) {

  pandoc.p(
    "No métier level 6 metiers met the selection and confidentiality criteria for this region and year."
  )

} else {

  # First row
  if (!is.na(CEtop6$CEmetier4[1])) {
    create_section4(CEtop6$CEmetier4[1], CEAREA, CLAREA)
  }

  if (!is.na(CEtop6$CEmetier5[1])) {
    create_section5(CEtop6$CEmetier5[1], CEAREA4, CLAREA4)
  }

  if (!is.na(CEtop6$CEmetier6[1])) {
    create_section6(CEtop6$CEmetier6[1], CEAREA6, CLAREA6)
  }

  # Remaining rows
  if (nrow(CEtop6) >= 2) {

    for (i in 2:nrow(CEtop6)) {

      if (!is.na(CEtop6$CEmetier4[i]) &&
          !is.na(CEtop6$CEmetier4[i - 1]) &&
          CEtop6$CEmetier4[i] != CEtop6$CEmetier4[i - 1]) {
        create_section4(CEtop6$CEmetier4[i], CEAREA, CLAREA)
      }

      if (!is.na(CEtop6$CEmetier5[i]) &&
          !is.na(CEtop6$CEmetier5[i - 1]) &&
          CEtop6$CEmetier5[i] != CEtop6$CEmetier5[i - 1]) {
        create_section5(CEtop6$CEmetier5[i], CEAREA4, CLAREA4)
      }

      if (!is.na(CEtop6$CEmetier6[i]) &&
          !is.na(CEtop6$CEmetier6[i - 1]) &&
          CEtop6$CEmetier6[i] != CEtop6$CEmetier6[i - 1]) {
        create_section6(CEtop6$CEmetier6[i], CEAREA6, CLAREA6)
        cat("\n")
      }
    }
  }
}



```




