---
title: "Multiannual overview template"
author: "RCG ISSG Regional overviews"
date: "1/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r ReadData, echo=FALSE, message=FALSE}
library(dplyr)
library(knitr)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(data.table)

#Choose RCG. Options: BA, NA, NSEA
RCG <- "BA"
years <- c(2015,2016,2017,2018,2019)

load(paste("Q:\\dfad\\data\\Data\\RDB\\RDB_RCG_",RCG,"_CL_CE_2009_2019_prepared_20200616\\RDB_RCG_",RCG,"_CE_2009_2019_prepared_20200616.Rdata", sep=""))
load(paste("Q:\\dfad\\data\\Data\\RDB\\RDB_RCG_",RCG,"_CL_CE_2009_2019_prepared_20200616\\RDB_RCG_",RCG,"_CL_2009_2019_prepared_20200616.Rdata", sep=""))

CE_years <- ce_rcg[ce_rcg$Year %in% years,]
CL_years <- cl_rcg[cl_rcg$Year %in% years,]


#Adds IDs [move to preparation]
cl_rcg[, FlagCountry_Loa := paste(FlagCountry, VesselLengthCategory, sep = "_")]
ce_rcg[, FlagCountry_Loa := paste(FlagCountry, VesselLengthCategory, sep = "_")]
# Add to preparation [and convert 2-letter code to 3-letter code]
#colnames(ce_rcg)[colnames(ce_rcg) == "LandingCountry"] <-
#  "LandingCountry2" # <-------------------------------------------------- No more LandingCountry in ce,lines to delete?
# for maps of foreign landings 'LandingCountry' is needed
ce_rcg[,LandingCountry := HarbourCountry]
#Filter
cl <- filter(cl_rcg, Year %in% years)

ce <- filter(ce_rcg, Year %in% years)

cl <- droplevels(cl)
ce <- droplevels(ce)

```


**RCG Multiannual overviews**

**CE and CL data Data**

Text describing the input data....

**Text describing figures 1**

## Figures 1: Effort {.tabset}
### Days at sea OTB fisheries
```{r echo=FALSE, message=FALSE}

DAS_country <- CE_years %>%
    group_by(Year, FlagCountry, FishingActivityLvl5) %>%
    summarise(DaysAtSea=sum(DaysAtSea))

DAS_country_OTB <- DAS_country[DAS_country$FishingActivityLvl5 %like% "OTB",]

ggplot(data=DAS_country_OTB, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country OTB fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))


```

### Days at sea Gillnet fisheries
```{r echo=FALSE, message=FALSE}


DAS_country <- CE_years %>%
    group_by(Year, FlagCountry, FishingActivityLvl5) %>%
    summarise(DaysAtSea=sum(DaysAtSea))

DAS_country_G <- DAS_country[DAS_country$FishingActivityLvl5 %like% "G",]

ggplot(data=DAS_country_G, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country Gillnet fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))



```

## {-}


**Text describing figures 2

## Figures 2 Landings {.tabset}
### Landings OTB fisheries
```{r echo=FALSE, message=FALSE}

Landings_country <- CL_years %>%
  group_by(Year, FlagCountry, FishingActivityLvl5) %>%
  summarise(LandingWeight_ton=sum(LandingWeight_ton))

Landings_country_OTB <- Landings_country[Landings_country$FishingActivityLvl5 %like% "OTB",]

ggplot(data=Landings_country_OTB, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country OTB -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))


```

### Landings Gillnet fisheries
```{r echo=FALSE, message=FALSE}

Landings_country <- CL_years %>%
  group_by(Year, FlagCountry, FishingActivityLvl5) %>%
  summarise(LandingWeight_ton=sum(LandingWeight_ton))

Landings_country_G <- Landings_country[Landings_country$FishingActivityLvl5 %like% "G",]

ggplot(data=Landings_country_G, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country Gillnet -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```
## {-}



**Text describing figures 3

## Figures 3: Landings {.tabset}
### Landing by country of main species  
```{r echo=FALSE, message=FALSE}


Landings_year_country <- cl %>% group_by(Year, Species, Quarter, FishingGround, FlagCountry) %>% summarise(LadingWeight_art_ton = sum(LandingWeight_ton), .groups = "drop" ) 

cl$yqtr<- paste(cl$Year, cl$Quarter, sep = "/")

Landings_year_country <- cl %>% group_by(Year, Species, yqtr, FlagCountry) %>% summarise(LadingWeight_art_ton = sum(LandingWeight_ton), .groups = "drop" ) 


Landings_yc_mainSpp_v1 <- subset(Landings_year_country, LadingWeight_art_ton > 500 )
#unique(Landings_yc_mainSpp_v1$Species)

Landings_yc_mainSpp_v2 <- subset(Landings_year_country, Species %in% c("Actinopterygii" ,"Ammodytes","Clupea harengus", "Coregonus albula", 
"Gadus morhua","Merlangius merlangus",  "Mytilus edulis", "Osmerus eperlanus","Perca fluviatilis", "Platichthys flesus","Pleuronectes platessa","Sprattus sprattus","Neogobius melanostomus","Abramis brama"))


ggplot(data=Landings_yc_mainSpp_v2, aes(Year, LadingWeight_art_ton, colour=FlagCountry)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~Species)+
  labs(title=paste("Landings by year & country - main species(Landings > 400tons) "), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))



```

### Landing by country of main species  
```{r echo=FALSE, message=FALSE}

ggplot(data=Landings_yc_mainSpp_v2, aes(Year, LadingWeight_art_ton, colour=Species)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```

### Landing by country of main species  
```{r echo=FALSE, message=FALSE}


ggplot(data=Landings_yc_mainSpp_v2, aes(Species, LadingWeight_art_ton, colour=Year)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))



```
## {-}


**Text describing figures 4

## Figures 4: Landings by country {.tabset}
### Landing of main species by country - DEU
```{r echo=FALSE, message=FALSE}

#unique(Landings_year_country$FlagCountry )

DEU <- subset(Landings_yc_mainSpp_v2, FlagCountry == 'DEU')
DNK <- subset(Landings_yc_mainSpp_v2, FlagCountry == 'DNK')
EST <- subset(Landings_yc_mainSpp_v2, FlagCountry == 'EST')
FIN <- subset(Landings_yc_mainSpp_v2, FlagCountry == 'FIN')
LTU <- subset(Landings_yc_mainSpp_v2, FlagCountry == 'LTU')
LVA <- subset(Landings_yc_mainSpp_v2, FlagCountry == 'LVA')
POL <- subset(Landings_yc_mainSpp_v2, FlagCountry == 'POL')
SWE <- subset(Landings_yc_mainSpp_v2, FlagCountry == 'SWE')



ggplot(data=DEU, aes(Species, LadingWeight_art_ton)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry + Year)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```

### Landing of main species by country - DNK
```{r echo=FALSE, message=FALSE}

ggplot(data=DNK, aes(Species, LadingWeight_art_ton)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry + Year)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```

### Landing of main species by country - EST
```{r echo=FALSE, message=FALSE}

ggplot(data=EST, aes(Species, LadingWeight_art_ton)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry + Year)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```

### Landing of main species by country - LTU
```{r echo=FALSE, message=FALSE}

ggplot(data=LTU, aes(Species, LadingWeight_art_ton)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry + Year)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```


### Landing of main species by country - LVA
```{r echo=FALSE, message=FALSE}

ggplot(data=LVA, aes(Species, LadingWeight_art_ton)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry + Year)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```

### Landing of main species by country - POL
```{r echo=FALSE, message=FALSE}

ggplot(data=POL, aes(Species, LadingWeight_art_ton)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry + Year)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```



### Landing of main species by country - SWE
```{r echo=FALSE, message=FALSE}

ggplot(data=SWE, aes(Species, LadingWeight_art_ton)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ FlagCountry + Year)+
  labs(title=paste("Landings by year & country - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```
## {-}


**Text describing figures 5

## Figures 5: Total Landings of Species {.tabset}
### Landing of main species  
```{r echo=FALSE, message=FALSE}

ggplot(data=Landings_yc_mainSpp_v2, aes(Year, LadingWeight_art_ton, colour=Species)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ Species)+
  labs(title=paste("Landings by year - main species"), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```
