


```{r title, include = F}
# Diferences with the regular Multiannual report:
# lines 97-99: we filter CL and CE with those vessels
# lines 149 - 150: we filter the fleer register with those vessels registered with GNS/GTR/GND as main gear
# effort and landings by vessel length category instead by fishing activity


RCG <- "RCG_BA" # RCG_NA, RCG_BA or RCG_NSEA
years <- c(2016,2017,2018,2019,2020,2021) 
if (RCG == "RCG_NA") {
  front_title <- paste("RDB Catch and Effort Overview North Atlantic ", sep = "")
  title_stock <- c('North Atlantic region')
 # warning_stock<-c('')
 # warning_uk<-c("Paragraph UK/Brexit") - no UK data is reported
} else if (RCG == "RCG_BA") {
  front_title <- paste("RDB Catch and Effort Overview Baltic ", sep = "")
  title_stock <- c('Baltic region')
 # warning_uk<-c("")
 # warning_stock<-c("Moreover some countries reported landings of herring from area 27.3.d.28. The group was not able to identify whether it was stock 'her.27.28' or 'her.27.25-2932'. As a temporary solution, all these landings were assigned to 'her.27.25-2932'.") - corrected after RCG 2021
} else if (RCG == "RCG_NSEA") {
  front_title <- paste("RDB Catch and Effort Overview North Sea and Eastern Arctic ", sep = "")
  title_stock <- c('North Sea and Eastern Arctic regions')
 # warning_stock<-c('')
 # warning_uk<-c("")
}
```


---
title: `r front_title`
author: "RCG ISSG Regional overviews"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---


<style type="text/css">

h1.title {
  font-size: 20px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo=FALSE}
if (RCG == "RCG_NA") {
  htmltools::img(src = knitr::image_uri(file.path("../../overviews_shiny/www/logo RCG NA NS_EA.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
} else if (RCG == "RCG_BA") {
  htmltools::img(src = knitr::image_uri(file.path("../../overviews_shiny/www/logo RCG BALTIC.PNG")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
} else if (RCG == "RCG_NSEA") {
  htmltools::img(src = knitr::image_uri(file.path("../../overviews_shiny/www/logo RCG NA NS_EA.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
}
```


```{r ReadData, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(knitr)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(data.table)
library(directlabels)
library(flextable)
library(scales)
library(DT)
library(gridExtra)
library(grid)
library(plotly)
source("../../funs/fun_theme_flextable.r")

#years <- c(2015,2016,2017,2018,2019)
year <- 2021 # 2021 OK for the fleet register
#data_dir <- paste("../../data/002_prepared/RCG_", RCG, "/", sep = '')
#data_dir <- paste("D:/Do przegrania na PC/IntersessionalWork/RCGs Data/2020 data/RCG_", RCG, "/", sep = '') #Marta's path
#data_dir <- paste("Q:/mynd/RDB/RDB_fisheries_overviews/data/002_prepared/RCG_", RCG, "/", sep = '')
# data_dir <- paste("D:/Documents/PNAB/2022/000_RCG_InterssessionalWork/ISSG_Catch_Effort_Sampling_overviews/ISSG_overviews/RegionalOverviews/input_data/2021/", RCG, "/", sep = '') # Ana's path PC
data_dir <- paste("C:/Use/0_Lucia/6_Working groups/RCG_ISSG/ISSG Catch and Effort Overview/ISSG_overviews/RDB_Data/2021/", RCG, "/", sep = '') # Lucia's path PC


load(paste(data_dir,"RDB_",RCG,"_CE_2009_2021_prepared_20220601.Rdata", sep=""))
load(paste(data_dir,"RDB_",RCG,"_CL_2009_2021_prepared_20220601.Rdata", sep=""))

#Nuno file with stocks
Def_stock <- read.delim("../../data/aux_stocks.txt")

CE_years <- ce_rcg[ce_rcg$Year %in% years,]
CL_years <- cl_rcg[cl_rcg$Year %in% years,]

# filter all fleet with metier GNS / GTR. 
CE_years <- subset(CE_years, substr(FishingActivityCategoryEuropeanLvl5,1,3) %in% c("GNS", "GTR"))
CL_years <- subset(CL_years, substr(FishingActivityCategoryEuropeanLvl5,1,3) %in% c("GNS", "GTR"))
		

DAS_country <- CE_years %>%
    group_by(Year, FlagCountry, VesselLengthCategory) %>%  # include VesselLengthCategory
    summarise(DaysAtSea=sum(DaysAtSea))
#DAS_country$gear <- substr(DAS_country$FishingActivityCategoryEuropeanLvl5,1,3)

Landings_country <- CL_years %>%
  group_by(Year, FlagCountry, VesselLengthCategory) %>%    # include VesselLengthCategory
  summarise(LandingWeight_ton=sum(LandingWeight_ton))
#Landings_country$gear <- substr(Landings_country$FishingActivityCategoryEuropeanLvl5,1,3)

#fleet register
# functions and packages
	require(data.table)

	fleetreg<-data.table()

		# based on full history
	
		# dir<-paste("D:/Documents/PNAB/2022/000_RCG_InterssessionalWork/ISSG_Catch_Effort_Sampling_overviews/ISSG_overviews/RegionalOverviews/data/fleet_reg/output/", year,"/", sep = "") ## PC Ana
		dir<-paste("C:/Use/0_GitHub/RCGs/RegionalOverviews/data/fleet_reg/output/", year,"/", sep = "") # Lucia's path PC
				
	
	for (ctry in c("BEL","DEU","DNK","ESP","EST","FIN","FRA","IRL","LTU","LVA","NLD","POL","PRT","SWE")) # no data for "GBR"
		{
		# print(ctry)
		fleetreg<-rbind(fleetreg,fread(paste(dir,ctry,"_export.csv", sep = ""), sep = ";",stringsAsFactors=FALSE, verbose=FALSE))
		}	

	 		# subsets data
		fleetreg<-fleetreg[License_Ind=="Y",]
			# creates status date date and combines data
		fleetreg$V2021<-0
		fleetreg$V2020<-0
		fleetreg$V2019<-0
		fleetreg$V2018<-0
		fleetreg$V2017<-0
		fleetreg$V2016<-0

		fleetreg[Event_Start_Date<=20210101 & Event_End_Date>=20210101,V2021:=20210101,]
		fleetreg[Event_Start_Date<=20200101 & Event_End_Date>=20200101,V2020:=20200101,]
		fleetreg[Event_Start_Date<=20190101 & Event_End_Date>=20190101,V2019:=20190101,]		
		fleetreg[Event_Start_Date<=20180101 & Event_End_Date>=20180101,V2018:=20180101,]
		fleetreg[Event_Start_Date<=20170101 & Event_End_Date>=20170101,V2017:=20170101,]
		fleetreg[Event_Start_Date<=20160101 & Event_End_Date>=20160101,V2016:=20160101,]
	
		fleetreg$Status_date<-0
	
		# filter all fleet with GNS / GTR as main gear in the register. 
		fleetreg <- subset(fleetreg, Gear_Main_Code %in% c("GNS", "GTR"))
		
		target_cols<-c("Country_Code","CFR","Event_Code","Event_Start_Date","Event_End_Date","License_Ind","Loa","Ton_Gt","Ton_Oth","Ton_Gts","Power_Main","Power_Aux","Status_date")
	
		df2021<-as.data.frame(fleetreg[V2021==20210101,])
		df2021$Status_date<-2021
		df2021<-df2021[target_cols]
		
		df2020<-as.data.frame(fleetreg[V2020==20200101,])
		df2020$Status_date<-2020
		df2020<-df2020[target_cols]
		
		df2019<-as.data.frame(fleetreg[V2019==20190101,])
		df2019$Status_date<-2019
		df2019<-df2019[target_cols]
		
		df2018<-as.data.frame(fleetreg[V2018==20180101,])
		df2018$Status_date<-2018
		df2018<-df2018[target_cols]
			
		df2017<-as.data.frame(fleetreg[V2017==20170101,])
		df2017$Status_date<-2017
		df2017<-df2017[target_cols]

		df2016<-as.data.frame(fleetreg[V2016==20160101,])
		df2016$Status_date<-2016
		df2016<-df2016[target_cols]
		
		fleetreg<-as.data.table(rbind(df2021, df2020, df2019, df2018, df2017, df2016))
			
		# a few formats and quality checks
		fleetreg$Power_Main<-as.numeric(fleetreg$Power_Main)
		fleetreg$Ton_Gt<-as.numeric(fleetreg$Ton_Gt)
		# QCA: should yield 0
#    	sum(is.na(fleetreg$Power_Main))
# 		sum(is.na(fleetreg$Ton_Gt))
		
		
## For the harmonization of the country colours between Annual and Multiannual overviews		
colour_table <-
  read.table(
    #"D:/Documents/PNAB/2022/000_RCG_InterssessionalWork/ISSG_Catch_Effort_Sampling_overviews/ISSG_overviews/RegionalOverviews//data/aux_colours.txt",
    "C:/Use/0_GitHub/RCGs/RegionalOverviews/data/aux_colours.txt",  # Lucia's PC
    header = T,
    sep = "\t",
    colClasses = "character",
    na.strings = "",
    comment.char = ""
  )
aux_colours_ggplot =  colour_table[,c("Country","colour5")]
		  		
```

**Disclaimer**

The tables and figures of the overviews presented in this document are made for the coordination of EU regional fisheries data collection purposes and are not designed for any other use. Data used for producing the outputs are extracted from the Regional Database (RDB) and EU Fleet Register. Dates of data extractions are stated in Appendix A. Due to different aggregations and reporting authorities, data can differ from those used e.g. for assessments or technical reports.
Member States (MS) are responsible for uploading latest data and the latest year should be viewed as provisional. Data can be resubmitted by a MS for more than one previous year so there might be differences in earlier year reports, if countries update back in time. Responsibility for the quality of the data and comparability to other data sources lies with the MS that provided these data. The upload logs presented by MS regarding the data submitted to RDB can be found in the ISSG Data Quality report.

The respective scripts and calculations used for data displaying are publicly available via the RCG GitHub (https://github.com/ices-eg/RCGs) and subject to change as the work of the group progresses.



# **RCG Multiannual overviews - Net fisheries (GNS, GTR)**

The present Catch and Effort Overview displays summary information on the EU fleet evolution (EU Fleet Register) and EU commercial landings (CL) and fishing effort (CE) statistics included in the Regional Data Base (RDB), which is used to store detailed commercial fisheries and sampling data. 
Only the net fisheries including GNS and GTR have been considered in this report.



##	Overall fleet evolution {.tabset}

The tables included in this section present a summary of the information on licensed vessels with GNS or GTR reported as main gear, from the European Union Fleet Register in the period 2016-2021.

### Number of vessels
**Table 1.** Number of licensed vessels with GNS or GTR reported as main gear, by flag country in the EU vessel register.
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}
res_fleetreg<-tapply(fleetreg$Country_Code,list(fleetreg$Country_Code,fleetreg$Status_date),length)
ft<-theme_flextable(res_fleetreg)
ft

```

### Power
**Table 2.** Power (`1000*`kW) of licensed vessels with GNS or GTR reported as main gear, by flag country in the EU vessel register.
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}
res_fleetreg_pwr<-round(tapply(fleetreg$Power_Main, list(fleetreg$Country_Code, fleetreg$Status_date), sum)/1000,1)
ft<-theme_flextable(res_fleetreg_pwr)
ft
```

### Gross tonnage
**Table 3.** Gross Tonnage (`1000*`GT) of licensed vessels with GNS or GTR reported as main gear, by flag country in the EU vessel register.
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}
res_fleetreg_gt <- round(tapply(fleetreg$Ton_Gt, list(fleetreg$Country_Code, fleetreg$Status_date), sum)/1000,1)
ft<-theme_flextable(res_fleetreg_gt)
ft
```

## {-}

##	RDB information for EU countries

The figures below are based on RDB effort (CE) and landings (CL) data. 

## Effort {.tabset}

The annual fishing effort for  net fisheries, in number of days at sea, for the `r title_stock`, is presented in the figures below. Since this is not a mandatory field in the reported CE data, there may be missing information for some countries/years. Information about missing information is given in Table 4.

The first panel ('Days at sea - Net fisheries') compiles the annual fishing effort for net fisheries, by flag country. 
The second panel ('Days at sea per vessel length category - Net fisheries') present the annual fishing effort for net fisheries, by flag country, for the different vessel length categories



**Table 4.** Summary of the missing information on the days at sea reported by country and year.
```{r echo=FALSE, message=FALSE, warning = FALSE, message=FALSE, out.width="90%", out.height="90%" }
## Days at sea Total fisheries -  Annual total fishing effort by country  
# missing data (Days at Sea) (Laura's table)
Missing <- CE_years %>% 
  group_by(Year, FlagCountry , is.na(DaysAtSea)) %>% 
  summarise(missing = n()) %>% 
  filter(`is.na(DaysAtSea)` == TRUE) %>% 
  select(FlagCountry, missing)

MissingDaysAtSea <- CE_years %>% 
  group_by(Year, FlagCountry) %>%  
  summarise(Total = n()) %>% 
  full_join(Missing)

PercentageMissingDaysAtSea <- MissingDaysAtSea %>% 
  group_by(Year, FlagCountry) %>% 
  summarise('%missingRecords (DaysAtSea)' = as.integer((missing/Total)*100)) %>% 
  arrange(FlagCountry) 

# Countries with no effort data 
PercentageMissingDaysAtSea2 <- subset(PercentageMissingDaysAtSea, !is.na(`%missingRecords (DaysAtSea)`))
PercentageMissingDaysAtSea2 <- PercentageMissingDaysAtSea %>% 
  filter(!is.na(`%missingRecords (DaysAtSea)`)) %>% 
  arrange(Year)

ft<-theme_flextable(PercentageMissingDaysAtSea2)
ft

```


### Days at sea - Net fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}
DAS_total <- CE_years %>%
    group_by(Year, FlagCountry) %>%
    summarise(DaysAtSea=sum(DaysAtSea))

dasTotal <- ggplot(data=DAS_total, aes(Year, round(DaysAtSea/1000,0), colour=FlagCountry)) + 
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_discrete(guide = 'none') +
  geom_dl(aes(label = FlagCountry), method = list(dl.trans(x = x + 0.1), "last.points", cex = 0.7))+
  labs(title=paste("Days at sea by country - Net fisheries -", RCG), x="year", y="Days at sea (thousands)", colour="Country") +
 theme(axis.text = element_text(size=9),plot.title=element_text(size=11), axis.title = element_text(size=9))

dasTotal <- dasTotal + scale_color_manual(breaks = aux_colours_ggplot$Country,
        values = aux_colours_ggplot$colour5)

ggplotly(dasTotal)

```

### Days at sea per vessel length category - Net fisheries

```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="95%", out.height="95%"}
#DAS_country_N <- droplevels(DAS_country[!is.na(DAS_country$DaysAtSea) & DAS_country$gear %in% c('GNS','GND','GTR'),])
DAS_country_N <- DAS_country

if (dim(DAS_country_N)[1]>0) {
dasCountryN <- ggplot(data=DAS_country_N, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_point() + geom_line() +
  theme_bw() +
  facet_wrap(~VesselLengthCategory, scales="free_y")+
  labs(title=paste("Days at sea by country - Net fisheries -", RCG), x="year", y="Days at sea", colour="Country")+
 theme(legend.position="bottom", axis.text.x = element_text(size=8),  axis.text.y = element_text(size=8),plot.title=element_text(size=11), axis.title = element_text(size=9),legend.title=element_text(size=10),legend.text=element_text(size=9),panel.spacing.x = unit(1,"lines"), panel.spacing.y = unit(2,"lines"))

dasCountryN <- dasCountryN + scale_color_manual(breaks = aux_colours_ggplot$Country,
        values = aux_colours_ggplot$colour5)

ggplotly(dasCountryN)
}

```

## {-}

## Landings {.tabset}

The annual landings overview for net fisherie, for the `r title_stock`, is presented in the interactive figures below. 
The first panel ('Landings - Net fisheries') compiles the annual total landings for net fisheries, by flag country. 
The second panel ('Landings per vessel length category - Net fisheries') presents the annual landings for net fisheries, by flag country, for the different vessel length categories



### Landings - Net fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

Landings_total <- CL_years %>%
  group_by(Year, FlagCountry) %>%
  summarise(LandingWeight_ton=sum(LandingWeight_ton))

landingsTotal <- ggplot(data=Landings_total, aes(Year, round(LandingWeight_ton/1000,0), colour=FlagCountry)) +
  geom_point() + geom_line() +
  scale_colour_discrete(guide = 'none') +
  geom_dl(aes(label = FlagCountry), method = list(dl.trans(x = x + 0.1), "last.points", cex = 0.7))+
  labs(title=paste("Landings by country - Net fisheries -", RCG), x="year", y="Landings (thousand ton)")+
  theme(axis.text.x = element_text(size=9), plot.title=element_text(size=11), axis.title = element_text(size=9))+
  theme_bw()

landingsTotal <- landingsTotal + scale_color_manual(breaks = aux_colours_ggplot$Country,
        values = aux_colours_ggplot$colour5)

ggplotly(landingsTotal)

```

### Landings per vessel length category - Net fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="95%", out.height="95%"}
#Landings_country_N <- droplevels(Landings_country[!is.na(Landings_country$LandingWeight_ton) & Landings_country$gear %in% c('GNS','GND','GTR'),])
Landings_country_N <- Landings_country

if (dim(Landings_country_N)[1]>0) {
landingsN <- ggplot(data=Landings_country_N, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_point() +geom_line() +
  theme_bw() +
  facet_wrap(~VesselLengthCategory, scales="free_y")+
  labs(title=paste("Landings by country - Net fisheries -", RCG), x="year", y="Landings (ton)", colour="Country")+
 theme(legend.position="bottom",  axis.text.x = element_text(size=8),  axis.text.y = element_text(size=8),plot.title=element_text(size=11), axis.title = element_text(size=9),legend.title=element_text(size=10),legend.text=element_text(size=9),panel.spacing.x = unit(1,"lines"), panel.spacing.y = unit(2,"lines")) 

landingsN <- landingsN + scale_color_manual(breaks = aux_colours_ggplot$Country,
        values = aux_colours_ggplot$colour5)

ggplotly(landingsN)
}

```


## Appendix A.           Dates of data extraction
The data referring to the present year was collected under the RCG 2022 data call for the 2021 data for the Baltic Sea, North Sea, Eastern Arctic and the North Atlantic regions and downloaded from the system on the 17th of April 2022 with the exception of information detailed in section “2. Overall Fleet Evolution” which was extracted from the EU Fleet Register (https://webgate.ec.europa.eu/fleet-europa/index_en) on the 11th of March 2022.



## Appendix B. Glossary for the country codes

```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

country_table <-  read.table(
    #"D:/Documents/PNAB/2022/000_RCG_InterssessionalWork/ISSG_Catch_Effort_Sampling_overviews/ISSG_overviews/RegionalOverviews/data/aux_countries.txt", # Ana's PC
    "C:/Use/0_GitHub/RCGs/RegionalOverviews/data/aux_countries.txt",
    header = T,
    sep = ",",
    colClasses = "character",
    na.strings = "",
    comment.char = ""
  )
 
table_out <- droplevels(country_table[country_table$ISO3Code %in% CL_years$FlagCountry | country_table$ISO3Code %in% CL_years$LandingCountry,])
table_out <- table_out[,c('Country','ISO3Code')]

kable(table_out, row.names=F, col.names = c('Name','Code'),format = "html", table.attr = "style='width:30%;'")

```


