---
title: "Multiannual overview template"
author: "RCG ISSG Regional overviews"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r ReadData, echo=FALSE, message=FALSE}
library(dplyr)
library(knitr)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(data.table)
library(directlabels)
#Choose RCG. Options: BA, NA, NSEA
RCG <- "NSEA"
years <- c(2015,2016,2017,2018,2019)
load(paste("Q:\\mynd\\RDB\\RDB_fisheries_overviews\\RDB_RCG_",RCG,"_CE_2009_2019_prepared_20200616.Rdata", sep=""))
load(paste("Q:\\mynd\\RDB\\RDB_fisheries_overviews\\RDB_RCG_",RCG,"_CL_2009_2019_prepared_20200616.Rdata", sep=""))
CE_years <- ce_rcg[ce_rcg$Year %in% years,]
CL_years <- cl_rcg[cl_rcg$Year %in% years,]

DAS_country <- CE_years %>%
    group_by(Year, FlagCountry, FishingActivityLvl5) %>%
    summarise(DaysAtSea=sum(DaysAtSea))
DAS_country$gear <- substr(DAS_country$FishingActivityLvl5,1,3)

Landings_country <- CL_years %>%
  group_by(Year, FlagCountry, FishingActivityLvl5) %>%
  summarise(LandingWeight_ton=sum(LandingWeight_ton))
Landings_country$gear <- substr(Landings_country$FishingActivityLvl5,1,3)

```


**RCG Multiannual overviews**

**CE and CL data Data**

Text describing the input data....

**Text describing figures 1**

## Figures 1: Effort {.tabset}

### Days at sea Total fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
DAS_total <- CE_years %>%
    group_by(Year, FlagCountry) %>%
    summarise(DaysAtSea=sum(DaysAtSea))

ggplot(data=DAS_total, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  labs(title=paste("Days at sea by country Total fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))



# idea to label
ggplot(data=DAS_total, aes(Year, DaysAtSea, colour=FlagCountry)) + 
  geom_line() +
  scale_colour_discrete(guide = 'none') +
  geom_dl(aes(label = FlagCountry), method = list(dl.trans(x = x + 0.1), "last.points", cex = 0.7))+
  labs(title=paste("Days at sea by country Total fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))




```

### Days at sea Bottom trawl fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
DAS_country_OTB <- DAS_country[DAS_country$gear %in% c('OTB','PTB','OTT'),]
ggplot(data=DAS_country_OTB, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country Bottom trawl fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Days at sea Midwater trawl fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
DAS_country_OTM <- DAS_country[DAS_country$gear %in% c('OTM','PTM'),]
ggplot(data=DAS_country_OTM, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country Midwater trawl fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Days at sea Demersal seine fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
DAS_country_S <- DAS_country[DAS_country$FishingActivityLvl5 %like% "S" ,]
ggplot(data=DAS_country_S, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country Demersal seine fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Days at sea Gillnet fisheries

```{r echo=FALSE, message=FALSE, warning = FALSE}
DAS_country_G <- DAS_country[DAS_country$gear %like% "G",]
ggplot(data=DAS_country_G, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country Gillnet fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Days at sea Longline fisheries

```{r echo=FALSE, message=FALSE, warning = FALSE}
DAS_country_L <- DAS_country[DAS_country$gear %like% "L",]
ggplot(data=DAS_country_L, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country Longline fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Days at sea Dredge fisheries

```{r echo=FALSE, message=FALSE, warning = FALSE}
DAS_country_D <- DAS_country[DAS_country$gear %like% "D",]
ggplot(data=DAS_country_D, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country Dredge fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Days at sea Pots and traps fisheries

```{r echo=FALSE, message=FALSE, warning = FALSE}
DAS_country_F <- DAS_country[DAS_country$gear %like% "F",]
ggplot(data=DAS_country_F, aes(Year, DaysAtSea, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Days at sea by country Pots and Traps fisheries -", RCG), x="year", y="Days at sea")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

## {-}



**Text describing figures 2

## Figures 2 Landings {.tabset}

### Landings Total fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}

Landings_total <- CL_years %>%
  group_by(Year, FlagCountry) %>%
  summarise(LandingWeight_ton=sum(LandingWeight_ton))

ggplot(data=Landings_total, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  labs(title=paste("Landings by country Total fisheries -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Landings Bottom trawl fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
Landings_country_OTB <- Landings_country[Landings_country$gear %in% c("OTB","PTB","OTT"),]
ggplot(data=Landings_country_OTB, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country Bottom trawl -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Landings Midwater trawl fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
Landings_country_OTM <- Landings_country[Landings_country$gear %in% c("OTM","PTM"),]
ggplot(data=Landings_country_OTM, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country Midwater trawl -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Landings Demersal seine fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
Landings_country_OTM <- Landings_country[Landings_country$FishingActivityLvl5 %like% "S",]
ggplot(data=Landings_country_OTM, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country Demersal seine -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Landings Gillnet fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
Landings_country_G <- Landings_country[Landings_country$FishingActivityLvl5 %like% "G",]
ggplot(data=Landings_country_G, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country Gillnet -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Landings Longline fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
Landings_country_G <- Landings_country[Landings_country$FishingActivityLvl5 %like% "L",]
ggplot(data=Landings_country_G, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country Longline -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Landings Dredge fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
Landings_country_G <- Landings_country[Landings_country$FishingActivityLvl5 %like% "D",]
ggplot(data=Landings_country_G, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country Dredge -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```

### Landings Pots and traps fisheries
```{r echo=FALSE, message=FALSE, warning = FALSE}
Landings_country_G <- Landings_country[Landings_country$FishingActivityLvl5 %like% "F",]
ggplot(data=Landings_country_G, aes(Year, LandingWeight_ton, colour=FlagCountry)) +
  geom_line() +
  theme_bw() +
  facet_wrap(~FishingActivityLvl5)+
  labs(title=paste("Landings by country Pots and traps -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))
```
## {-}



**Text describing figures 3

## Figures 3: Landings {.tabset}
### 1 Total landings top 10 species - line  
```{r echo=FALSE, message=FALSE, warning = FALSE}
CL_years$Species1 <- as.character(CL_years$Species)
top10_species <- CL_years %>%
  group_by(Species1) %>%
  summarise(lwTot=sum(LandingWeight_ton)) %>%
  arrange(desc(lwTot)) %>%
  top_n(10)
top10_species$Top10species <- "X"
landings_sp <- left_join(CL_years,top10_species,by="Species1")
landings_sp$topSpecies <- ifelse(is.na(landings_sp$Top10species),"Other species",landings_sp$Species1)

landings_sp_sum <- landings_sp %>%
  group_by(Year, topSpecies) %>%
  summarise(Landing_ton=sum(LandingWeight_ton))

ggplot(data=landings_sp_sum, aes(Year, Landing_ton, colour=topSpecies)) +
  geom_line() +
  labs(title=paste("Landings by top 10 species -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```

### 2 Total landings top 10 species - stacked bar   
```{r echo=FALSE, message=FALSE, warning = FALSE}
CL_years$Species1 <- as.character(CL_years$Species)
top10_species <- CL_years %>%
  group_by(Species1) %>%
  summarise(lwTot=sum(LandingWeight_ton)) %>%
  arrange(desc(lwTot)) %>%
  top_n(10)
top10_species$Top10species <- "X"
landings_sp <- left_join(CL_years,top10_species,by="Species1")
landings_sp$topSpecies <- ifelse(is.na(landings_sp$Top10species),"Other species",landings_sp$Species1)

landings_sp_sum <- landings_sp %>%
  group_by(Year, topSpecies) %>%
  summarise(Landing_ton=sum(LandingWeight_ton))

ggplot(data=landings_sp_sum, aes(x=Year, y=Landing_ton, fill=topSpecies)) +
  geom_bar(position="stack", stat="identity") +
  labs(title=paste("Landings by top 10 species -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```


### 3 Total landings top 10 species - stacked bar pct
```{r echo=FALSE, message=FALSE, warning = FALSE}
CL_years$Species1 <- as.character(CL_years$Species)
top10_species <- CL_years %>%
  group_by(Species1) %>%
  summarise(lwTot=sum(LandingWeight_ton)) %>%
  arrange(desc(lwTot)) %>%
  top_n(10)
top10_species$Top10species <- "X"
landings_sp <- left_join(CL_years,top10_species,by="Species1")
landings_sp$topSpecies <- ifelse(is.na(landings_sp$Top10species),"Other species",landings_sp$Species1)

landings_sp_sum <- landings_sp %>%
  group_by(Year, topSpecies) %>%
  summarise(Landing_ton=sum(LandingWeight_ton))

ggplot(data=landings_sp_sum, aes(x=Year, y=Landing_ton, fill=topSpecies)) +
  geom_bar(position="fill", stat="identity") +
  labs(title=paste("Landings by top 10 species -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```

###  Landings by country top 10 species - stacked bar pct
```{r echo=FALSE, message=FALSE, warning = FALSE}
CL_years$Species1 <- as.character(CL_years$Species)
top10_species <- CL_years %>%
  group_by(Species1) %>%
  summarise(lwTot=sum(LandingWeight_ton)) %>%
  arrange(desc(lwTot)) %>%
  top_n(10)
top10_species$Top10species <- "X"
landings_sp <- left_join(CL_years,top10_species,by="Species1")
landings_sp$topSpecies <- ifelse(is.na(landings_sp$Top10species),"Other species",landings_sp$Species1)

landings_sp_sum <- landings_sp %>%
  group_by(Year, FlagCountry, topSpecies) %>%
  summarise(Landing_ton=sum(LandingWeight_ton))

ggplot(data=landings_sp_sum, aes(x=Year, y=Landing_ton, fill=FlagCountry)) +
  geom_bar(position="fill", stat="identity") +
  theme_bw() +
  facet_wrap(~topSpecies)+
  labs(title=paste("Landings by top 10 species -", RCG), x="year", y="Landings (ton)")+
  theme(axis.text.x = element_text(size=8), plot.title=element_text(size=8), axis.title = element_text(size=8))

```
## {-}

