---
title: "RDBES Catch and Effort Overview"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output:
  html_document:
    toc: true
    
params:
  set_subtitle: "Title"
  region: 'Baltic'
  year: 2023
  logo_path: "../../overviews_shiny/www/logo RCG BALTIC.PNG"
  data_dir: '../../data_RDBES/002_prepared/20240129/RCG_BA'
  RDBES_download_date: '01/01/2000'
  CLfileName: 'RDBES_RCG_BA_CL_2021_2021_prepared_20240129'
  CEfileName: 'RDBES_RCG_BA_CE_2021_2021_prepared_20240129'
  
---

---
subtitle: `r paste(params$region, params$year, sep = ", ")`
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo=FALSE}
  htmltools::img(src = knitr::image_uri(params$logo_path), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px;',width="300px", height="100px")
```

```{r loadPackages, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD PACKAGES AND DEFINE EVAL_PARAMETERS IF NEEDED

# library(tidyverse)
# library(car)
# library(ggrepel)
# library(knitr)
# library(kableExtra)
# library(data.table)
# library(magrittr)
# library(plotly)
# library(leaflet)

 ## establish conditions  - can use it if for example some chunks should be run only for selected Regions, e.g. only Bal
 eval_region <- params$region=='Baltic' # when added to the chunk header, the chunk will be run only for Baltic report

```


```{r GlobalSettings, echo=FALSE}
# DEFINE GLOBAL PARAMETERS/FUNCTIONS FOR DISPLAYING TABLES/PLOTS/MAPS/...

```

```{r loadFunctions, echo=FALSE}
# LOAD FUNCTIONS GENERATING PLOTS/MAPS

```

```{r mapData, echo=FALSE}
# LOAD AND PREPARE DATA NEEDED FOR MAPS (shp, rdata, ...)

```

```{r loadPrepareData, echo=FALSE}
# LOAD AND PREPARE DATA

source('scripts/loadData.R', local = knitr::knit_global())
  
```

```{r fleetRegisterData, echo=FALSE}
# LOAD AND PREPARE FLEET REGISTER DATA

```




**Disclaimer**
put some text here

# Introduction
put some text here

## Reading the graphs
### Barplots
put some text here

### Maps
put some text here

# Overall fleet evolution (All RCGs){.tabset}

## Number of vessels
**Table 1.**put some text here
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

```

## Power
**Table 2.** put some text here
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

```

## Gross tonnage
**Table 3.** put some text here
```{r echo=FALSE, message=FALSE, warning = FALSE, out.width="90%", out.height="90%"}

```


# Landings (CL)

## Overall landings

### Landings by species {.tabset}
#### species
#### species and country


### Landings by catch_group {.tabset}
#### catch group
#### catch_group and country

### Landings by fleet

### Landings by area {.tabset}
#### area
#### area and country
#### country and area

### Landings by metier {.tabset}
#### metier lvl5
#### metier lvl5 and country
#### metier lvl6
#### metier lvl6 and country

### Landings by harbour {.tabset}
#### harbour
#### harbour and flag country
#### map - harbour
#### map - harbour and flag country

### Landings abroad

### Spatial distribution of landings


## Small pelagics landings

### Landings by country, small pelagics

### Landings by species, small pelagics {.tabset}
#### species
#### species and country

### Landings by fleet, small pelagics {.tabset}
#### fleet
#### country and fleet
#### fleet and country

### Landings by area, small pelagics {.tabset}
#### area
#### area and country
#### country and area
#### map area
#### map area and flag country

### Landings by metier, small pelagics {.tabset}
#### metier lvl5
#### metier lvl5 and country
#### metier lvl6
#### metier lvl6 and country

### Landings by harbour, small pelagics {.tabset}
#### harbour
#### harbour and flag country
#### map - harbour
#### map - harbour and flag country

### Landings abroad, small pelagics

### Spatial distribution of landings, small pelagics


## Demersal landings (without flatfish)

### Landings by country, demersal (without flatfish)

### Landings by species, demersal (without flatfish) {.tabset}
#### species
#### species and country

### Landings by fleet, demersal (without flatfish) {.tabset}
#### fleet
#### country and fleet
#### fleet and country

### Landings by area, demersal (without flatfish) {.tabset}
#### area
#### area and country
#### country and area
#### map area
#### map area and flag country

### Landings by metier, demersal (without flatfish) {.tabset}
#### metier lvl5
#### metier lvl5 and country
#### metier lvl6
#### metier lvl6 and country

### Landings by harbour, demersal (without flatfish) {.tabset}
#### harbour
#### harbour and flag country
#### map - harbour
#### map - harbour and flag country

### Landings abroad, demersal (without flatfish)

### Spatial distribution of landings, demersal (without flatfish)


## Flatfish landings

### Landings by country, flatfish

### Landings by species, flatfish {.tabset}
#### species
#### species and country

### Landings by fleet, flatfish {.tabset}
#### fleet
#### country and fleet
#### fleet and country

### Landings by area, flatfish {.tabset}
#### area
#### area and country
#### country and area
#### map area
#### map area and flag country

### Landings by metier, flatfish {.tabset}
#### metier lvl5
#### metier lvl5 and country
#### metier lvl6
#### metier lvl6 and country

### Landings by harbour, flatfish {.tabset}
#### harbour
#### harbour and flag country
#### map - harbour
#### map - harbour and flag country

### Landings abroad, flatfish

### Spatial distribution of landings, flatfish


# Effort (CE)

## Effort by country {.tabset}
### number of trips
### days at sea
### KW-days
### GT-days

## Effort by fleet {.tabset}
### number of trips
### number of trips by country and fleet
### number of trips by fleet and country

## Effort by area
### Below 10 meters {.tabset}
#### area
#### area and country
#### country and area

### 10 meteres and above {.tabset}
#### area
#### area and country
#### country and area


## Effort by metier
### Below 10 meters  {.tabset}
#### metier lvl 5
#### metier lvl 5 and country
#### statistical rectangle

### 10 meteres and above  {.tabset}
#### metier lvl 5
#### metier lvl 5 and country
#### statistical rectangle

## Effort by harbour
### Below 10 meters {.tabset}
#### harbour
#### harbour and country
#### map - harbour

### 10 meteres and above {.tabset}
#### harbour
#### harbour and country
#### map - harbour

## Spatal distribution on effort {.tabset}
### Below 10 meters
### 10 meteres and above

## Appendix A. Dates of data extraction
## Appendix B. Catch groups
## Appendix C. Mean Landings per stock, put years here
## Appendix D. Summary information of the landings abroad (ton), by country and area
## Appendix E. Glossary for the country codes

