
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
# Need to set the root directory because the working directory is forced for each chunk to the directory of the rmd
# knitr::opts_knit$set(root.dir = "C:/Users/madamowicz/Documents/GitHub/RCGs/Metiers")
knitr::opts_knit$set(root.dir = "C:/Users/molla004/OneDrive - Wageningen University & Research/Git/hub/RCGs/Metiers")
```

# Description of metier assignment script workflow

This documents explains the metier assignment workflow implemented in the R script developed during work of RCG ISSG Metier issues. Every step of the data analysis is described below. 

## Including libraries
```{r libraries, message = FALSE, warning = FALSE}
library(stringr)
library(data.table)
library(openxlsx)
library(purrr)
library(lubridate)
```

```{r lib2,echo = FALSE}
library(knitr)
library(kableExtra)
```


```{r clean_enironment, results='hide', echo=FALSE}
rm(list=ls())
gc()
```

## Importing functions
Import all functions from files located in the *Functions* folder.
```{r import_functions, results='hide'}
for(f in list.files(path="./Scripts/Functions", full.names = T)){
  source(f)
}
rm(f)
```

## Loading input data
Input data should follow the format developed during the work of ISSG and should be saved as csv file.
```{r load_input_data}
data.file <- "data_input_example.csv"
input.data <- loadInputData(data.file)
rm(data.file)
```

```{r, echo=FALSE}
kable(input.data[1:5,])%>%
  kable_styling() %>%
  scroll_box(width = "100%")
```

## Input data format validation

The *validateInputDataFormat* function checks if all columns defined in the data format are present in the input data set and if they are of a correct data type. If any of the columns defined in the data format are not present, the function fill stop executing and return an error. If any column has different type than expected then the function will return a warning. If there are additional columns not included in the data format, the function will return a warning. If any of the columns are factors the function will return an error.

```{r validate_input_data_format}
validateInputDataFormat(input.data)
```

## Loading reference lists
The following code will import reference lists from the GitHub repository.

* areas,
* species,
* metiers,
* gear.

```{r reference_lists}
url <- "https://github.com/ices-eg/RCGs/raw/master/Metiers/Reference_lists/AreaRegionLookup.csv"
area.list <- loadAreaList(url)
url <- "https://github.com/ices-eg/RCGs/raw/master/Metiers/Reference_lists/Metier%20Subgroup%20Species%202020.xlsx"
species.list <- loadSpeciesList(url)
url <- "https://github.com/ices-eg/RCGs/raw/master/Metiers/Reference_lists/RDB_ISSG_Metier_list.csv"
metier.list <- loadMetierList(url)
url <- "https://github.com/ices-eg/RCGs/raw/master/Metiers/Reference_lists/Code-ERSGearType-v1.1.xlsx"
gear.list <- loadGearList(url)
assemblage.list <- unique(c(species.list$species_group, species.list$dws_group))
assemblage.list <- assemblage.list[!is.na(assemblage.list)]
rm(url)
```

## Input data codes validation

The *validateInputDataCodes* function validates the codes in the columns: area, gear, gearFR, selection, registered_target_assemblage, FAO_species, measure. If any of the above mentioned columns contains invalid etries then the function gives a warning.

```{r validate_input_data_codes}
validateInputDataCodes(input.data, gear.list, area.list, species.list)
```


## Input data preparation
**Basic conversions/recodings**

```{r basic_conversions}
input.data[,EUR:=as.numeric(EUR)]
input.data[,KG:=as.numeric(KG)]
input.data[,c("selection_type","selection_mesh"):=data.table(str_split_fixed(selection,"_",2))]
input.data[,selection_type:=ifelse(selection_type=="",NA,selection_type)]
input.data[,selection_mesh:=ifelse(selection_mesh=="",NA,selection_mesh)]
```

**Assign RCG names to the input data**

```{r arealist}
input.data <- merge(input.data, area.list, all.x = T, by = "area")
```

**Assign species categories to the input data**

```{r specieslist}
input.data <- merge(input.data, species.list, all.x = T, by = "FAO_species")
```

**Assign gear group and recoded gear name to the input data**

```{r gearlist}
input.data<-merge(input.data, gear.list, all.x = T, by.x = "gear", by.y = "gear_code")
```


```{r newtab, echo=FALSE}
kable(input.data[1:5,])%>%
  kable_styling() %>%
  scroll_box(width = "100%")
```

## Process input data

**Fishing sequence definition**

In a variable called sequence.def please include all columns that will constitute a fishing sequence. This variable will be used as a key for grouping operations later in the script.

```{r fishing_sequence}
sequence.def <- c("Country","year","vessel_id","vessel_length","trip_id","haul_id",
                  "fishing_day","area","ices_rectangle","gear_level6","mesh","selection",
                  "registered_target_assemblage")
```

**Calculation of group totals for fishing sequences**

```{r group_totals}
input.data[,":="(seq_group_KG = sum(KG, na.rm = T),
                 seq_group_EUR = sum(EUR, na.rm = T)),
           by=c(sequence.def,"species_group")]
```

**Selecting a measure**

Select a measure to determine the dominant group at a sequence level. If at least one species in a sequence has "value" in a measure column then all species in that sequence get the same measure.

```{r sequence_measure}
input.data[,":="(seq_measure = getMeasure(measure)),by=sequence.def]
```

**Finding the dominant group for each sequence**

```{r dominant_species_group}
input.data[seq_measure == "weight",
           ":="(seq_dom_group = species_group[which.max(seq_group_KG)]),
           by=sequence.def]
input.data[seq_measure == "value",
           ":="(seq_dom_group = species_group[which.max(seq_group_EUR)]),
           by=sequence.def]

```

```{r newtab2, echo=FALSE}
kable(input.data[order(vessel_id,trip_id,fishing_day,area,ices_rectangle,gear,mesh),][1:5])%>%
  kable_styling() %>%
  scroll_box(width = "100%")

input.data[,":="(seq_group_KG=NULL,seq_group_EUR=NULL,seq_measure=NULL)]
```

**Apply DWS rules**

If DWS species weight/value is more than 8% of the total wegiht/value in a fishing sequence and a gear/RCG combination is applicable to DWS rules then the dominant group of species in that fishing sequence is changed to DWS.

```{r dws_rules}
input.data[dws_group=="DWS",seq_DWS_kg:=sum(KG, na.rm = T),
           by=c(sequence.def, "dws_group")]
input.data[,seq_total_kg:=sum(KG, na.rm = T),
           by=sequence.def]
input.data[,seq_DWS_perc:=ifelse(is.na(seq_DWS_kg),0,seq_DWS_kg/seq_total_kg)*100]
input.data[,seq_DWS_perc:=max(seq_DWS_perc),by=sequence.def]
input.data[,DWS_gear_applicable:=grepl(RCG,DWS_for_RCG),by=.(RCG)]
input.data[seq_DWS_perc>8 & DWS_gear_applicable,seq_dom_group:="DWS"]
input.data[,":="(dws_group=NULL,DWS_for_RCG=NULL,seq_DWS_kg=NULL,seq_total_kg=NULL,seq_DWS_perc=NULL,
                 DWS_gear_applicable=NULL)]

```

## Assign metier level 6

Function called getMetier executes row by row and returns metier level 5 and level 6, based on RCG, gear, target assemblage, mesh size and selection device. If it is not possible to find a metier then the function returns MIS_MIS and MIS_MIS_0_0_0.

```{r assing_metier_lvl6}
input.data$metier_level_6<-NA
input.data$metier_level_5<-NA
input.data[,c("metier_level_6","metier_level_5"):=pmap_dfr(list(RCG,
                                          year,
                                          gear_level6, 
                                          registered_target_assemblage,
                                          seq_dom_group, 
                                          mesh, 
                                          selection_type,
                                          selection_mesh), getMetier)]
```

```{r newtab3, echo=FALSE}
kable(input.data[order(vessel_id,trip_id,fishing_day,area,ices_rectangle,gear,mesh),][1:5])%>%
  kable_styling() %>%
  scroll_box(width = "100%")
```

## Missing metiers

Function *missingMetiersByLevel* is executed for search levels defined. The function tries to find a metier in case metiers starting with "MIS" were assigned in the previous step. In case of a success, the function returns new metier level 5 and level 6 together with a number of sequences of the new metier and a search level used.

**Step 1. Target assemblage and gear group**

```{r missing_metiers_step1}
input.data[,":="(month=month(dmy(fishing_day)),
                 quarter=quarter(dmy(fishing_day)))]
step.levels<-list(c("vessel_id","month","area","seq_dom_group","gear_group"),
                  c("vessel_id","month","area","seq_dom_group"),
                  c("vessel_id","quarter","area","seq_dom_group","gear_group"),
                  c("vessel_id","quarter","area","seq_dom_group"),
                  c("vessel_id","year","area","seq_dom_group","gear_group"),
                  c("vessel_id","year","area","seq_dom_group"),
                  c("vessel_id","month","seq_dom_group","gear_group"),
                  c("vessel_id","month","seq_dom_group"),
                  c("vessel_id","quarter","seq_dom_group","gear_group"),
                  c("vessel_id","quarter","seq_dom_group"),
                  c("vessel_id","year","seq_dom_group","gear_group"),
                  c("vessel_id","year","seq_dom_group"))
for(level in step.levels){
  if(nrow(input.data[substr(metier_level_6,1,3)=="MIS"])>0){
    input.data <- missingMetiersByLevel(input.data,level,sequence.def)
  } else {break}
}
```

**Step 2. Gear and gear group**

```{r missing_metiers_step2}
step.levels<-list(c("vessel_id","month","area","gear_level6"),
                  c("vessel_id","quarter","area","gear_level6"),
                  c("vessel_id","year","area","gear_level6"),
                  c("vessel_id","month","gear_level6"),
                  c("vessel_id","quarter","gear_level6"),
                  c("vessel_id","year","gear_level6"),
                  c("vessel_id","month","area","gear_group"),
                  c("vessel_id","quarter","area","gear_group"),
                  c("vessel_id","year","area","gear_group"),
                  c("vessel_id","month","gear_group"),
                  c("vessel_id","quarter","gear_group"),
                  c("vessel_id","year","gear_group"))
for(level in step.levels){
  if(nrow(input.data[substr(metier_level_6,1,3)=="MIS"])>0){
    input.data <- missingMetiersByLevel(input.data,level,sequence.def)
  } else {break}
}
```
 
**Step 3. Vessel length group and target assemblage**
 
```{r missing_metiers_step3}
input.data[,vessel_length_group:=cut(vessel_length,breaks=c(0,10,12,18,24,40,Inf),right=F)]
step.levels<-list(c("month","vessel_length_group","gear_FR","area","seq_dom_group"),
                  c("month","gear_FR","area","seq_dom_group"),
                  c("quarter","vessel_length_group","gear_FR","area","seq_dom_group"),
                  c("quarter","gear_FR","area","seq_dom_group"),
                  c("year","vessel_length_group","gear_FR","area","seq_dom_group"),
                  c("year","gear_FR","area","seq_dom_group"),
                  c("month","vessel_length_group","gear_FR","seq_dom_group"),
                  c("month","gear_FR","seq_dom_group"),
                  c("quarter","vessel_length_group","gear_FR","seq_dom_group"),
                  c("quarter","gear_FR","seq_dom_group"),
                  c("year","vessel_length_group","gear_FR","seq_dom_group"),
                  c("year","gear_FR","seq_dom_group"))
for(level in step.levels){
  if(nrow(input.data[substr(metier_level_6,1,3)=="MIS"])>0){
    input.data <- missingMetiersByLevel(input.data,level,sequence.def)
  } else {break}
}
```

**Step 4. Vessel length group, gear, and gear group**

```{r missing_metiers_step4}

step.levels<-list(c("month","vessel_length_group","gear_FR","area","gear_level6"),
                  c("month","gear_FR","area","gear_level6"),
                  c("quarter","vessel_length_group","gear_FR","area","gear_level6"),
                  c("quarter","gear_FR","area","gear_level6"),
                  c("year","vessel_length_group","gear_FR","area","gear_level6"),
                  c("year","gear_FR","area","gear_level6"),
                  c("month","vessel_length_group","gear_FR","gear_level6"),
                  c("month","gear_FR","gear_level6"),
                  c("quarter","vessel_length_group","gear_FR","gear_level6"),
                  c("quarter","gear_FR","gear_level6"),
                  c("year","vessel_length_group","gear_FR","gear_level6"),
                  c("year","gear_FR","gear_level6"),
                  c("month","vessel_length_group","gear_FR","area","gear_group"),
                  c("month","gear_FR","area","gear_group"),
                  c("quarter","vessel_length_group","gear_FR","area","gear_group"),
                  c("quarter","gear_FR","area","gear_group"),
                  c("year","vessel_length_group","gear_FR","area","gear_group"),
                  c("year","gear_FR","area","gear_group"),
                  c("month","vessel_length_group","gear_FR","gear_group"),
                  c("month","gear_FR","gear_group"),
                  c("quarter","vessel_length_group","gear_FR","gear_group"),
                  c("quarter","gear_FR","gear_group"),
                  c("year","vessel_length_group","gear_FR","gear_group"),
                  c("year","gear_FR","gear_group"))
for(level in step.levels){
  if(nrow(input.data[metier_level_6=="MIS_MIS_0_0_0"])>0){
    input.data <- missingMetiersByLevel(input.data,level,sequence.def)
  } else {break}
}
```


```{r newtab4, echo=FALSE}
kable(input.data[order(mis_met_number_of_seq,vessel_id,trip_id,fishing_day,area,ices_rectangle,gear,mesh),][1:5])%>%
  kable_styling() %>%
  scroll_box(width = "100%")
```

## Vessel patterns
Vessel patterns analysis tries to find a common metier list for a vessel and year which will create a pattern. Then the pattern will be used to replace rare metiers with the best matched common metiers at the specified search level.

**Specify the percentage threshold of the number of sequences below which a metier will be considered rare**

```{r rare_treshold}
rare.threshold <- 15
```

**Identify rare metiers**

Function *rareMetiersLvl5* attributes a metier with a "rare" or "common" label based on the specified threshold.

```{r rare_metiers}
input.data<-rareMetiersLvl5(input.data,sequence.def,rare.threshold)
```

```{r newtab5, echo=FALSE}
kable(input.data[order(vessel_id,trip_id,fishing_day,area,ices_rectangle,gear,mesh),][1:10])%>%
  kable_styling() %>%
  scroll_box(width = "100%")
```

**Apply vessel patterns on rare metiers**

Function *vesselPatternsByLevel* is executed for search levels defined. The function tries to find the best matched matier from patter for the rare metiers, based on search levels passed as parameters. In case of a success, the function returns metier level 5 from pattern together with a number of sequences of the pattern metier and a search level used.

Step 1. Target assemblage and gear group

```{r vessel_patterns_step1}
step.levels<-list(c("vessel_id","month","area","seq_dom_group","gear_group"),
                  c("vessel_id","month","area","seq_dom_group"),
                  c("vessel_id","quarter","area","seq_dom_group","gear_group"),
                  c("vessel_id","quarter","area","seq_dom_group"),
                  c("vessel_id","year","area","seq_dom_group","gear_group"),
                  c("vessel_id","year","area","seq_dom_group"),
                  c("vessel_id","month","seq_dom_group","gear_group"),
                  c("vessel_id","month","seq_dom_group"),
                  c("vessel_id","quarter","seq_dom_group","gear_group"),
                  c("vessel_id","quarter","seq_dom_group"),
                  c("vessel_id","year","seq_dom_group","gear_group"),
                  c("vessel_id","year","seq_dom_group"))
for(level in step.levels){
  if(nrow(input.data[metier_level_5_status=="rare" & is.na(metier_level_5_pattern)])>0){
    input.data <- vesselPatternsByLevel(input.data,level,sequence.def)
  } else {break}
}
```

Step 2. Gear and gear group

```{r vessel_patterns_step2}
step.levels<-list(c("vessel_id","month","area","gear_level6"),
                  c("vessel_id","quarter","area","gear_level6"),
                  c("vessel_id","year","area","gear_level6"),
                  c("vessel_id","month","gear_level6"),
                  c("vessel_id","quarter","gear_level6"),
                  c("vessel_id","year","gear_level6"),
                  c("vessel_id","month","area","gear_group"),
                  c("vessel_id","quarter","area","gear_group"),
                  c("vessel_id","year","area","gear_group"),
                  c("vessel_id","month","gear_group"),
                  c("vessel_id","quarter","gear_group"),
                  c("vessel_id","year","gear_group"))
for(level in step.levels){
  if(nrow(input.data[metier_level_5_status=="rare" & is.na(metier_level_5_pattern)])>0){
    input.data <- vesselPatternsByLevel(input.data,level,sequence.def)
  } else {break}
}
```

```{r, echo=FALSE}
kable(input.data[order(vessel_id,trip_id,fishing_day,area,ices_rectangle,gear,mesh),][1:10])%>%
  kable_styling() %>%
  scroll_box(width = "100%")
```

**Assign metier level 6 to metier level 5 from pattern**

Function called *metiersLvl6ForLvl5pattern* tries to find the best matched metier level 6 for metier level 5 from pattern which was assigned in the previous step. The function takes a search level as a parameter. It returns a metier level 6 together with the number of sequences and search level used.

```{r metier_level6_to_metier_level5}
input.data[,metier_level_6_pattern:=NA]
step.levels<-list(c("vessel_id","month","area","metier_level_5"),
                  c("vessel_id","quarter","area","metier_level_5"),
                  c("vessel_id","year","area","metier_level_5"),
                  c("vessel_id","month","metier_level_5"),
                  c("vessel_id","quarter","metier_level_5"),
                  c("vessel_id","year","metier_level_5"))
for(level in step.levels){
  if(nrow(input.data[metier_level_5_status=="rare" & 
                     !is.na(metier_level_5_pattern) &
                     is.na(metier_level_6_pattern)])>0){
    input.data <- metiersLvl6ForLvl5pattern(input.data,level,sequence.def)
  } else {break}
}
```

```{r newtab6, echo=FALSE}
kable(input.data[order(vessel_id,trip_id,fishing_day,area,ices_rectangle,gear,mesh),
               .(Country,RCG,year,vessel_id,vessel_length,trip_id,haul_id,fishing_day,area,ices_rectangle,gear,gear_FR,mesh,selection,FAO_species,
                 registered_target_assemblage,KG,EUR,metier_level_6,mis_met_level,mis_met_number_of_seq,
                 metier_level_5,metier_level_5_status,
                 metier_level_5_pattern,ves_pat_level,ves_pat_number_of_seq,
                 metier_level_6_pattern,ves_pat_met6_level,ves_pat_met6_number_of_seq)])%>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "300px")
```

**Find metier codes with more precise mesh size ranges and replace the ">0_0_0" metier codes if possible.**

Create new metier columns where rare metiers are replaced with the ones found in the pattern.

```{r new_metier_columns}
input.data[,":="(metier_level_5_new=ifelse(is.na(metier_level_5_pattern),
                                           metier_level_5,
                                           metier_level_5_pattern),
                 metier_level_6_new=ifelse(is.na(metier_level_6_pattern),
                                           metier_level_6,
                                           metier_level_6_pattern))]
```

Function called *detailedMetiersLvl6ForLvl5* replaces ">0_0_0" metiers with more precise metiers.

```{r replace_zero_metiers}
input.data[,detailed_metier_level_6:=ifelse(grepl("_>0_0_0",metier_level_6_new),NA,metier_level_6_new)]
step.levels<-list(c("vessel_id","month","area","metier_level_5_new"),
                  c("vessel_id","quarter","area","metier_level_5_new"),
                  c("vessel_id","year","area","metier_level_5_new"),
                  c("vessel_id","month","metier_level_5_new"),
                  c("vessel_id","quarter","metier_level_5_new"),
                  c("vessel_id","year","metier_level_5_new"))
for(level in step.levels){
  if(nrow(input.data[is.na(detailed_metier_level_6)])>0){
    input.data <- detailedMetiersLvl6ForLvl5(input.data,level,sequence.def)
  } else {break}
}
```

```{r newtab7, echo=FALSE}
kable(input.data[order(vessel_id,trip_id,fishing_day,area,ices_rectangle,gear,mesh),
                .(Country,RCG,year,vessel_id,vessel_length,trip_id,haul_id,fishing_day,area,ices_rectangle,gear,gear_FR,mesh,selection,FAO_species,
                  registered_target_assemblage,KG,EUR,metier_level_6,mis_met_level,mis_met_number_of_seq,
                  metier_level_5,metier_level_5_status,
                  metier_level_5_pattern,ves_pat_level,ves_pat_number_of_seq,
                  metier_level_6_pattern,ves_pat_met6_level,ves_pat_met6_number_of_seq,metier_level_6_new,
               detailed_metier_level_6,det_met6_number_of_seq,det_met6_level)][order(det_met6_number_of_seq)][1:10])%>% 
kable_styling() %>%
scroll_box(width = "100%")
```


## Explanation of the result columns

* *metier_level_5* and *metier_level_6* - metier codes assigned in the first step by the *getMetier* function. In the next step the *missingMetiersByLevel* is called which tries to replace "MIS" metier codes with the best matched metier codes using the specified search levels,

* *mis_met_level* and *mis_met_number_of_seq* - if the *missingMetiersByLevel* succeeds to replace "MIS" metier code then it gives the information on the level where the metier was found together with the number of fishing sequences for that metier. Initially assigned non-"MIS" metiers have empty values in these columns. Only "MIS" metiers which have been replaced with new codes have non-empty values in these columns,

* *metier_level_5_status* - label indicating whether the metier code in the *metier_level_5* column is considered rare given the specified threshold. These is determined by the *rareMetiersLvl5* function, 

* *metier_level_5_pattern* - the metier level 5 codes found in the vessel pattern for metiers level 5 labeled as rare in the previous step. This is done by the *vesselPatternByLevel* function,

* *ves_pat_level* and *ves_pat_number_of_seq* - if the *vesselPatternByLevel* function succeeds to find the metier in the vessel pattern then it gives the information on the level where the metier was found together with the number of fishing sequences for that metier,

* *metier_level_6_pattern* - the best matched metier level 6 code from the vessel pattern given the metier level 5 from pattern and the specified search level. The value in this column is returned by the *metierLvl6ForLvl5pattern*,

* *ves_pat_met6_level* and *ves_pat_met6_number_of_seq* - the *metierLvl6ForLvl5pattern* function returns the information on the level where the metier was found together with the number of fishing sequences for that metier,

* *metier_level_5_new* and *metier_level_6_new* - values in these columns contain the metiers found by *getMetier* completed by *missingMetiersByLevel* or metiers returned from the vessel pattern which replaced rare metiers,

* *detailed_metier_level_6* - the best matched metier level 6 with more precise mesh size ranges which replaces the ">0_0_0" metiers. This step is done by the *detailedMetiersLvl6ForLvl5*,

* *det_met6_number_of_seq* and *det_met6_level* - if the *detailedMetiersLvl6ForLvl5* function succeeds to find the metier with more precise mesh size range then it gives the information on the level where the metier was found together with the number of fishing sequences for that metier.

